%\nocite{273ba834}
%\nocite{797789bc}
In this section, we are first and foremost concerned with relating two given categories in some way.
Of course, this should mean that we map objects to objects and morphisms to morphisms in a structure-preserving way.
Since the only structure a category has is its identities and composition, this means that identities are mapped to identities and that mapping morphisms to morphisms preserves composition.
In other words, it shouldn't matter if we first compose and then map, or the other way around.
With this in mind, we define functors: a set $F$ is a \textbf{functor} or \textbf{functorial} if it is a $4$-tuple consisting of a category $\mathbf{C}$, a category $\mathbf{C_{\alpha}}$, a function $F_{\mathrm{ob}} \colon \mathrm{ob}_{\mathbf{C}} \rightarrow \mathrm{ob}_{\mathbf{C}_{\alpha}}$, and a function
\begin{align*}
  F_{\mathrm{mor}}
  &\colon
  \mathrm{ob}_{\mathbf{C}}
  \times
  \mathrm{ob}_{\mathbf{C}}
  \rightarrow
  \bigcup_{X_{1},X_{2} \in \mathrm{ob}_{\mathbf{C}}}
  \left\lbrace
    f
    \colon
    \mathrm{mor}_{\mathbf{C}}(X_{1},X_{2})
    \rightarrow
    \mathrm{mor}_{\mathbf{C}_{\alpha}}
    (F_{\mathrm{ob}}(X_{1}),F_{\mathrm{ob}}(X_{2}))
  \right\rbrace
\end{align*}
which maps $(X_{1},X_{2})$ to a function
\begin{align*}
  F_{\mathrm{mor}}(X_{1},X_{2})
  \colon
  \mathrm{mor}_{\mathbf{C}}(X_{1},X_{2})
  \rightarrow
  \mathrm{mor}_{\mathbf{C}_{\alpha}}
  (F_{\mathrm{ob}}(X_{1}),F_{\mathrm{ob}}(X_{2}))
\end{align*}
such that
\begin{enumerate}
\item[(F1)]
the formula
\begin{align*}
  F_{\mathrm{mor}}(X,X)(\mathrm{id}_{X})
  &=
  \mathrm{id}_{F_{\mathrm{ob}}(X)}
\end{align*}
holds
\item[(F2)]
the formula
\begin{align*}
  F_{\mathrm{mor}}(X_{1},X_{3})(f_{23} \circ f_{12})
  &=
  F_{\mathrm{mor}}(X_{2},X_{3})(f_{23})
  \circ
  F_{\mathrm{mor}}(X_{1},X_{2})(f_{12})
\end{align*}  
holds
\end{enumerate}
Instead of {\glqq}a functor $F := (\mathbf{C},\mathbf{C}_{\alpha},F_{\mathrm{ob}},F_{\mathrm{mor}})${\grqq}, we also write {\glqq}a functor $F \colon \mathbf{C} \rightarrow \mathbf{C}_{\alpha}${\grqq}.
For a functor $F \colon \mathbf{C} \rightarrow \mathbf{C}_{\alpha}$, we call $\mathbf{C}$ the \textbf{domain (of $F$)} and $\mathbf{C}_{\alpha}$ the \textbf{codomain (of $F$)}.
This defines the assignments $\mathrm{dom_{F}}$ and $\mathrm{cod_{F}}$, which assign a functor its domain and codomain, respectively.
$\mathrm{dom_{F}}$ is called the \textbf{(functor) domain (assignment)} and $\mathrm{cod_{F}}$ is called the \textbf{(functor) codomain (assignment)}.
A functor with domain $\mathrm{dom_{F}}(F)$ and codomain $\mathrm{cod_{F}}(F)$ is referred to as a functor from $\mathrm{dom_{F}}(F)$ to $\mathrm{cod_{F}}(F)$.
In a not-so-slight abuse of notation, we will usually write $F$ for both $F_{\mathrm{ob}}$ and $F_{\mathrm{mor}}(X_{1},X_{2})$, a bit like the (C3) trick from remark \ref{rem:c3trick}.
However, experience shows that this actually improves both comprehensibility and readability.
Thus, it seems reasonable to adopt this notation in spite of it all.
The functor properties then read
\begin{enumerate}
\item[(F1)]
$F(\mathrm{id}_{X}) = \mathrm{id}_{F(X)}$
\item[(F2)]
$F(f_{23} \circ f_{12}) = F(f_{23}) \circ F(f_{12})$
\end{enumerate}
Essentially, to define a functor, one has to say what is assigned to objects and what is assigned to morphisms.
So, to define a functor $F$, we use a schema similar to functions
\begin{align*}
  F
  \colon
  \mathbf{C}
  &\rightarrow
  \mathbf{C}_{\alpha}
  \\
  X
  &\mapsto
  F_{\mathrm{ob}}(X)
  \\
  f_{12}
  &\mapsto
  F_{\mathrm{mor}}(X_{1},X_{2})(f_{12})
\end{align*}
or more sketchily
\begin{align*}
  X
  &\mapsto
  F_{\mathrm{ob}}(X)
  \\
  f_{12}
  &\mapsto
  F_{\mathrm{mor}}(X_{1},X_{2})(f_{12})
\end{align*}
if the domain and codomain are clear.
A rather important functor is the functor $\mathrm{id}_{\mathbf{C}} \colon \mathbf{C} \rightarrow \mathbf{C}$, which just assigns any object and morphism to itself.
$\mathrm{id}_{\mathbf{C}}$ is called the \textbf{identity (of $\mathbf{C}$)}.
In general, functors have the nice property that they can be composed in a sensible way.
Sensible in the sense that the composition is induced by function composition, $\circ^{1} := \circ$.
So, in accordance with functions, let us define an assignment $\circ^{2}$ by assigning to a pair of functors $(F_{\alpha\beta},F_{\beta\gamma})$ such that
\begin{align*}
  \mathrm{cod}(F_{\alpha\beta})
  &=
  \mathrm{dom}(F_{\beta\gamma})
\end{align*}
a functor
\begin{align*}
  \circ^{2}(F_{\alpha\beta},F_{\beta\gamma})
  \colon
  \mathbf{C}_{\alpha}
  &\rightarrow
  \mathbf{C}_{\gamma}
  \\
  X^{\alpha}
  &\mapsto
  F_{\beta\gamma}(F_{\alpha\beta}(X^{\alpha}))
  \\
  f_{12}^{\alpha}
  &\mapsto
  F_{\beta\gamma}(F_{\alpha\beta}(f_{12}^{\alpha}))
\end{align*}
It is easy to see that this is a functor by going through the definition of a functor.
The assignment $\circ^{2}$ is called \textbf{(functor) composition}, while $\circ^{2}(F_{\alpha\beta},F_{\beta\gamma})$ is called the \textbf{composition of $F_{\alpha\beta}$ and $F_{\beta\gamma}$} or \textbf{$F_{\beta\gamma}$ composed with $F_{\alpha\beta}$}.
The latter terminology suggests writing $F_{\beta\gamma} \circ^{2} F_{\alpha\beta}$ for $\circ^{2}(F_{\alpha\beta},F_{\beta\gamma})$.
Experience shows that it is safe to denote $\circ^{2}$ simply as $\circ$, just like with functions.
Functor composition clearly satisfies
\begin{align*}
  \left(
    F_{\gamma\delta}
    \circ
    F_{\beta\gamma}
  \right)
  \circ
  F_{\alpha\beta}
  &=
  F_{\gamma\delta}
  \circ
  \left(
    F_{\beta\gamma}
    \circ
    F_{\alpha\beta}
  \right)
\end{align*}
as a consequence of the associativity of function composition.
Furthermore, composing an arbitrary functor $F_{\alpha\beta}$ with the identity of $\mathbf{C}_{\alpha}$ and $\mathbf{C}_{\beta}$, respectively, trivially satisfies
\begin{align*}
  F_{\alpha\beta}
  \circ
  \mathrm{id}_{\mathbf{C}_{\alpha}}
  &=
  F_{\alpha\beta}
  =
  \mathrm{id}_{\mathbf{C}_{\beta}}
  \circ
  F_{\alpha\beta}
\end{align*}
as one would expect from an identity.
After seeing these properties, one might wonder if there is a category whose objects are categories and whose morphisms are the functors between them.
Before answering this question, let's slide in a quick example.
Since functors resemble\footnote{we return to this idea in subsection \ref{sec:hls}} functions, there are some apparent candidates for functors.
\\
\begin{exa}
\label{exa:basicsfuncs1}
Similar to functions, the most basic kinds of functors besides the identity should be the constant one, the inclusion, and the restriction functor.
\begin{enumerate}
\item[(a)]
We start with constant functors.
A functor $\mathrm{C}_{X^{\alpha}} \colon \mathbf{C} \rightarrow \mathbf{C}_{\alpha}$ is \textbf{constant (on $\mathbf{C}$ with target $X^{\alpha}$)} if for all $X$, the equation $X^{\alpha} = \mathrm{C}_{X^{\alpha}}(X)$ holds, and if for all $X_{1},X_{2}$ and all $f_{12}$, the equation $\mathrm{id}_{X^{\alpha}} = \mathrm{C}_{X^{\alpha}}(f_{12})$ holds.
$\mathrm{c}_{X^{\alpha}}$ will denote the special case of the constant functor on $\mathbf{1}_{X^{\alpha}}$ with target $X^{\alpha}$.
\item[(b)]
A subcategory $\mathbf{S}$ of $\mathbf{C}$ can be included in a functorial way.
Formally, the functor is just
\begin{align*}
  \mathrm{I}
  &:=
  \left(
    \mathcal{S},
    \mathcal{C},
    \mathrm{i}_{\mathrm{ob}},
    \mathrm{i}_{\mathrm{mor}},
  \right)
\end{align*}
with
\begin{align*}
  \mathrm{i}_{\mathrm{ob}}
  &\colon
  \mathrm{ob}_{\mathbf{S}}
  \rightarrow
  \mathrm{ob}_{\mathbf{C}}
  \\
  \mathrm{i}_{\mathrm{mor}}(X_{1},X_{2})
  &\colon
  \mathrm{mor}_{\mathbf{S}}(X_{1},X_{2})
  \rightarrow
  \mathrm{mor}_{\mathbf{C}}(X_{1},X_{2})
\end{align*}
each being the appropriate inclusion function.
$\mathrm{I}$ is called the \textbf{inclusion (of $\mathbf{S}$ in $\mathbf{C}$)}.
\item[(c)]
A functor $F \colon \mathbf{C} \rightarrow \mathbf{C}_{\alpha}$ can be restricted to a subcategory $\mathbf{S}$ of $\mathbf{C}$ by restricting $F_{\mathrm{ob}}$ to $\mathrm{ob}_{\mathbf{S}}$ while restricting $F_{\mathrm{mor}}$ to $\mathrm{ob}_{\mathbf{S}} \times \mathrm{ob}_{\mathbf{S}}$ and $F_{\mathrm{mor}}(X_{1},X_{2})$ to $\mathrm{mor}_{\mathbf{S}}(X_{1},X_{2})$.
Of course, the domain has to be adjusted to $\mathbf{S}$.
The resulting functor is denoted $F \vert \mathbf{S}$ and is called the \textbf{restriction of $F$ (to $\mathbf{S}$)}.
\end{enumerate}
\end{exa}
\begin{prf}
This is a straightforward exercise to learn how to deal with the notion of functors.
\\
\phantom{proven}
\hfill
$\square$
\end{prf}
Now, is there a category of categories? In TG, this is a paradox due to size issues, which is solved as usual by restricting to a Grothendieck universe.
The result is the (locally small) category $\mathbf{Cat}$, whose object set is the set of all small categories, and whose morphism function is defined by letting $\mathrm{mor}_{\mathbf{Cat}}(\mathbf{C}_{\alpha},\mathbf{C}_{\beta})$ be all the functors from $\mathbf{C}_{\alpha}$ to $\mathbf{C}_{\beta}$ (where these categories are assumed small, of course).
Composition is given by
\begin{align*}
  \circ_{\mathbf{Cat}}
  (\mathbf{C}_{\alpha},\mathbf{C}_{\beta},\mathbf{C}_{\gamma})
  (F_{\alpha\beta},F_{\beta\gamma})
  &:=
  F_{\beta\gamma}
  \circ
  F_{\alpha\beta}
\end{align*}
for $\mathbf{C}_{\alpha},\mathbf{C}_{\beta},\mathbf{C}_{\gamma}$ small.
What needs a little bit of proof is that $\mathrm{mor}_{\mathbf{Cat}}(\mathbf{C}_{\alpha},\mathbf{C}_{\beta})$ is a small set.
This becomes clear from the observation that for a functor $F \colon \mathbf{C}_{\alpha} \rightarrow \mathbf{C}_{\beta}$, we have
\begin{align*}
  F_{\mathrm{ob}}
  &\in
  \mathrm{mor}_{\mathbf{Set}}
  (\mathrm{ob}_{\mathbf{C}_{\alpha}},\mathrm{ob}_{\mathbf{C}_{\beta}})
  \\
  F_{\mathrm{mor}}(X_{1}^{\alpha},X_{2}^{\alpha})
  &\in
  \mathrm{mor}_{\mathbf{Set}}
  \left(
    \mathrm{mor}_{\mathbf{C}_{\alpha}}(X_{1}^{\alpha},X_{2}^{\alpha}),
    \mathrm{mor}_{\mathbf{C}_{\beta}}
    (F_{\mathrm{ob}}(X_{1}^{\alpha}),F_{\mathrm{ob}}(X_{2}^{\alpha}))
  \right)
\end{align*}
$\mathbf{Cat}$ is called the \textbf{category of (small) categories}.
In $\mathbf{Cat}$, it is clear what the inverse of a functor is.
And this idea can be extended to arbitrary functors between not necessarily small categories.
So, going back to the general case, a functor $F_{\alpha\beta}$ is said to have an \textbf{inverse $F_{\beta\alpha}$} if
\begin{align*}
  F_{\beta\alpha}
  \circ
  F_{\alpha\beta}
  &=
  \mathrm{id}_{\mathbf{C}_{\alpha}}
  \\
  F_{\alpha\beta}
  \circ
  F_{\beta\alpha}
  &=
  \mathrm{id}_{\mathbf{C}_{\alpha}}
\end{align*}
And for an inverse $F_{\beta\alpha}$ of $F_{\alpha\beta}$, we write $F_{\alpha\beta}^{-1}$, following the morphism case.
Further, $F_{\alpha\beta}$ is then called an \textbf{isomorphism (of categories from $\mathbf{C}_{\alpha}$ to $\mathbf{C}_{\beta}$)}, and the two categories $\mathbf{C}_{\alpha}$, $\mathbf{C}_{\beta}$ are said to be \textbf{isomorphic}, and we may write
\begin{align*}
  \mathbf{C}_{\alpha}
  &\cong
  \mathbf{C}_{\beta}
\end{align*}
In TG, for all pairs of categories $(\mathbf{C}_{\alpha},\mathbf{C}_{\beta})$, one can find a Grothendieck universe in which they are small and consider $\mathbf{Cat}$ w.r.t. this Grothendieck universe to equivalently define what isomorphism means.
Here is a good place to continue example \ref{exa:algstruct1} about algebraic structures.
\\
\begin{exa}
\label{exa:algstruct2}
Given monoids $M_{1},M_{2} \in \mathrm{ob}_{\mathbf{Mon}}$, a morphism $(M_{1},M_{2},\phi) \in \mathrm{mor}_{\mathbf{Mon}}(M_{1},M_{2})$ is in its essence nothing but a functor $F \colon \mathbf{B}M_{1} \rightarrow \mathbf{B}M_{2}$ and vice versa via
\begin{align*}
  \phi
  &=
  F_{\mathrm{mor}}
\end{align*}
Since we have only one-object categories, there is only one possibility for functors on objects.
The rest of the proof is a technicality.
The same reasoning applies to groups, noting that for a morphism $\phi$ in $\mathbf{Grp}$, one actually does not have to demand
\begin{align*}
  \phi
  \circ
  \mathrm{inv}
  &=
  \mathrm{inv}
  \circ
  \phi
\end{align*}
This is automatic from the other properties of groups.
As a full subcategory of $\mathbf{Cat}$, we can define a category $\mathbf{Mon}_{\mathrm{F}}$ whose objects are $\mathbf{B}M$ for all $M \in \mathrm{ob}_{\mathbf{Mon}}$ and whose morphisms are all functors $F \colon \mathbf{B}M_{1} \rightarrow \mathbf{B}M_{2}$ for $M_{1},M_{2} \in \mathrm{ob}_{\mathbf{Mon}}$.
We further get a full subcategory of $\mathbf{Mon}_{\mathrm{F}}$ by shrinking the object set to consist of categories which correspond to groups.
Let us denote this category $\mathbf{Grp}_{\mathrm{F}}$.
What is missing to make the example complete is an understanding of how $\mathbf{Mon}$ is essentially the same as $\mathbf{Mon}_{\mathrm{F}}$, and similarly for $\mathbf{Grp}$.
And it's not hard to see that these categories are isomorphic (w.r.t. some larger universe).
This is more of a technicality, since we have already seen that we have a bijection on objects and a bijection on morphisms.
\\
Also note that given types $\mathfrak{t}_{1} \colon Y_{1} \rightarrow \mathbb{N}$ and $\mathfrak{t}_{2} \colon Y_{2} \rightarrow \mathbb{N}$ and a bijection $b \colon Y_{1} \rightarrow Y_{2}$ such that
\begin{align*}
  \mathfrak{t}_{1}
  &=
  \mathfrak{t}_{2}
  \circ
  b
\end{align*}
then
\begin{align*}
  \mathbf{AS}_{\mathfrak{t}_{1}}
  &\cong
  \mathbf{AS}_{\mathfrak{t}_{2}}
\end{align*}
This means that the type of an algebraic structure is structurally only interesting up to isomorphism.
\end{exa}
\begin{prf}
The idea must suffice.
The technicalities can be seen as an exercise.
\\
\phantom{proven}
\hfill
$\square$
\end{prf}
Another example we will find useful is from topology.
\\
\begin{exa}
\label{exa:topology}
The idea behind a topology is to define a notion of which elements of a set are near each other.
This is nicely outlined in the first chapter of \cite{797789bc}.
But we also want to emphasize at this point that we think this fails a bit.
We will explain why later in this example.
On the other hand, we won't dig very deep, but will rather just write down the parts of point-set topology we need.
So, given a set $Y$, a subset $\mathfrak{T}_{Y} \subset \mathfrak{P}(Y)$ is a \textbf{topology (on $Y$)} if:
\begin{enumerate}
\item[(T1)]
the empty set $\emptyset$ and $Y$ itself are elements of $\mathfrak{T}_{Y}$
\item[(T2)]
any union of elements of $\mathfrak{T}_{Y}$ is an element of $\mathfrak{T}_{Y}$
\item[(T3)]
any finite intersection of elements of $\mathfrak{T}_{Y}$ is an element of $\mathfrak{T}_{Y}$
\end{enumerate}
A set $Y$ together with a topology $\mathfrak{T}_{Y}$ on $Y$ is called a \textbf{(topological) space}, and given a topological space
\begin{align*}
  Y
  &\doteq
  (Y,\mathfrak{T}_{Y})
\end{align*}
elements of $Y$ are called \textbf{points (of $Y$)}, while elements of $\mathfrak{T}_{Y}$ are called \textbf{open (sets of $Y$)}.
The topology of a topological space is often left implicit, and one only writes the set on which the topology is defined.
We will do so too.
After the definition, let's discuss why we think that topological spaces in general fail to fully describe nearness:
\begin{enumerate}
\item[$\bullet$]
In a general space $Y$, it can happen that for distinct points $y_{1},y_{2} \in Y$ - that is, $y_{1} \neq y_{2}$ - there is no $U_{1} \in \mathfrak{T}_{Y}$ such that $y_{1} \in U_{1}$ and $y_{2} \notin U_{1}$, but there is a $U_{2} \in \mathfrak{T}_{Y}$ such that $y_{2} \in U_{2}$ and $y_{1} \notin U_{2}$.
This asymmetry suggests that $y_{2}$ is arbitrarily near to $y_{1}$ but $y_{1}$ is not arbitrarily near to $y_{2}$.
This is odd for a good notion of nearness.
\end{enumerate}
In applications, such oddities are often excluded.
For example, in classical homotopy theory, one rarely works with non-Fr\'e{ch}et spaces (separation axiom $\textrm{T}_{1}$), since some things just don't work for them.
And this is perhaps due to the oddities of this notion of nearness.
\\
Topological spaces seem to be excellent as objects of a category.
But what should we take as morphisms?
It seems reasonable to take functions that preserve the topology somehow.
There are two possibilities for such functions when given topological spaces $(Y_{1},\mathfrak{T}_{Y_{1}})$, $(Y_{2},\mathfrak{T}_{Y_{2}})$:
\begin{enumerate}
\item[(1)]
The geometric way: a function $f \colon Y_{1} \rightarrow Y_{2}$ is \textbf{continuous (from $(Y_{1},\mathfrak{T}_{Y_{1}})$ to $(Y_{2},\mathfrak{T}_{Y_{2}})$)} if for all $y_{1} \in Y_{1}$ and all $V_{2} \in \mathfrak{T}(Y_{2})$ with $f(y_{1}) \in V_{2}$, there is a $V_{1} \in \mathfrak{T}(Y_{1})$ with $y_{1} \in V_{1}$ such that $f(V_{1}) \subset V_{2}$.
This generalizes the idea that a function is continuous if we can draw it in one stroke.
While this seems like the correct notion of continuity, it can only be as good as the notion of nearness we use.
And as we have argued, topological spaces are not perfect for that purpose, so we expect a broken notion of continuity in some cases.
\item[(2)]
The algebraic way: a function $f \colon Y_{1} \rightarrow Y_{2}$ is \textbf{continuous (from $(Y_{1},\mathfrak{T}_{Y_{1}})$ to $(Y_{2},\mathfrak{T}_{Y_{2}})$)} if $f^{-1}$ maps $\mathfrak{T}_{Y_{2}}$ into $\mathfrak{T}_{Y_{1}}$, that is, the preimage under $f$ of an open set is always open.
This definition is motivated by lattices\footnote{a lattice is a certain poset category that need not concern us here}, since topologies are lattices, and continuous functions defined in this way are precisely the lattice-preserving functions.
This is the idea picked up in \cite{797789bc}.
\end{enumerate}
Both definitions of continuous functions can be shown to be equivalent.
Now we have everything in place to define a new category: the category $\mathbf{Top}$, whose objects are topological spaces (up to size issues) and whose morphisms are all continuous functions composed via standard function composition (using the (C3) trick).
This works since composing continuous functions yields another continuous function.
$\mathbf{Top}$ is called the \textbf{category of (small) topological spaces}.
In the following, we list some notions around topological spaces that we will need.
\begin{enumerate}
\item[$\bullet$]
Now, for a space $(Y,\mathfrak{T}_{Y})$ and a subset $S \subset Y$, the topological space $(S,\mathfrak{T}_{Y} \vert S)$ with
\begin{align*}
  \mathfrak{T}_{Y} \vert S
  :=
  \lbrace
      V
      \in
      \mathfrak{P}(S)
    \,
    \vert
    \,
      V
      =
      S
      \cap
      U
      \text{ for }
      U
      \in
      \mathfrak{T}_{Y}
  \rbrace
\end{align*}
is called a \textbf{subspace (of $(Y,\mathfrak{T}_{Y})$)}.
\item[$\bullet$]
There are a bunch of subcategories of $\mathbf{Top}$ that will concern us later.
Namely, there is a category
\begin{align*}
  \mathbf{Open}_{Y}
  &\doteq
  \mathbf{Open}_{(Y,\mathfrak{T}_{Y})}
\end{align*}
whose object set is just the topology $\mathfrak{T}_{Y}$ and whose morphisms are only the continuous inclusions.
$\mathbf{Open}_{(Y,\mathfrak{T}_{Y})}$ is called the \textbf{category of open sets (of $(Y,\mathfrak{T}_{Y})$)}.
It will be convenient to make some notational agreements regarding the morphisms of this category.
For objects
\begin{align*}
  U,
  U_{1},
  U_{2}
  &\in
  \mathrm{ob}_{\mathbf{Open}_{Y}}
\end{align*}
with $U_{1} \subset U_{2}$, the unique morphism of
\begin{align*}
  \mathrm{mor}_{\mathbf{Open}_{Y}}(U_{1},U_{2})
\end{align*}
will be denoted
\begin{align*}
  \mathrm{i}(U_{1},U_{2})
  &\doteq
  \mathrm{i}^{Y}(U_{1},U_{2})
\end{align*}
or more specifically
\begin{align*}
  \mathrm{i}_{U}
  &\doteq
  \mathrm{i}_{U}^{Y}
  \doteq
  \mathrm{i}^{Y}(U,Y)
\end{align*}
Most often when needed, we will simplify this notation even further depending on the context.
\item[$\bullet$]
We need the notion of a cover of a space, and this is exactly what one would guess: a bunch of subsets of a space whose union contains the entire space.
Formally, given a topological space $Y$, a subset $\mathfrak{D}$ of $\mathfrak{P}(Y)$ is a \textbf{cover (of $Y$)} if
\begin{align*}
  Y
  \subset
  \bigcup
  \mathcal{D}
\end{align*}
while a cover $\mathfrak{D}$ of $(Y,\mathfrak{T}_{Y})$ is called \textbf{open} if $\mathfrak{D} \subset \mathfrak{T}_{Y}$.
Open covers are useful for treating a space locally.
This is often necessary in topology and algebraic topology.
Therefore, it will be convenient to have some more terminology around this concept.
An injective function
\begin{align*}
  \mathrm{cov}_{Y}
  &\in
  \mathrm{mor}_{\mathbf{Set}}
  \left(
    K,
    \mathrm{ob}_{\mathbf{Open}_{Y}}
  \right)
\end{align*}
is called an \textbf{open cover generator (of $Y$)} if
\begin{align*}
  Y
  \subset
  \bigcup_{k \in K}
  \mathrm{cov}_{Y}(k)
\end{align*}
On the other hand, an open cover $\mathfrak{D}$ of $Y$ gives rise to an open cover generator in a canonical way via self-indexing:
\begin{align*}
  \mathrm{cov}_{\mathfrak{D}}
  \doteq
  \mathrm{cov}_{Y}[\mathfrak{D}]
  \colon
  \mathfrak{D}
  &\rightarrow
  \mathrm{ob}_{\mathbf{Open}_{Y}}
  \\
  U
  &\mapsto
  U
\end{align*}
We usually abbreviate notation according to
\begin{align*}
  U_{k}
  \doteq
  U_{k}^{Y}
  &\doteq
  \mathrm{cov}_{Y}(k)
\end{align*}
for all $k \in K$ for an open cover generator $\mathrm{cov}_{Y}$.
Moreover, let us agree that for $a \in \mathbb{G}$ and a space $Y$, the function
\begin{align*}
  \mathrm{cov}_{Y}^{a}
  &\in
  \mathrm{mor}_{\mathbf{Set}}
  \left(
    K_{a},
    \mathrm{ob}_{\mathbf{Open}_{Y}}
  \right)
\end{align*}
denotes an open cover generator of $Y$, while
\begin{align*}
  U_{k^{a}}
  \doteq
  U_{k^{a}}^{Y}
  &\doteq
  \mathrm{cov}_{Y}^{a}(k^{a})
\end{align*}
for all $k^{a} \in K_{a}$.
Now $\mathrm{cov}_{Y}$ gives rise to a full subcategory $\mathbf{Open}_{Y}^{\mathrm{cov}_{Y}}$ of $\mathbf{Open}_{Y}$ by restricting the object set to
\begin{align*}
  \mathrm{ob}_{\mathbf{Open}_{Y}^{\mathrm{cov}_{Y}}}
  &:=
  \left\lbrace
      U
      \in
      \mathrm{ob}_{\mathbf{Open}_{Y}}
    \,
    \vert
    \,
      \exists
      k
      \in
      K
      \text{ such that }
      U
      =
      \mathrm{cov}_{Y}(k)
  \right\rbrace
\end{align*}
Open covers can be ordered.
To this end, we call $\mathrm{cov}_{Y}^{\alpha}$ a \textbf{refinement of $\mathrm{cov}_{Y}$} if for all $k^{\alpha} \in K_{\alpha}$ there is a $k \in K$ such that
\begin{align*}
  \mathrm{cov}_{Y}^{\alpha}
  \left(
    k^{\alpha}
  \right)
  \subset
  \mathrm{cov}_{Y}(k)
\end{align*}
Refinement preorders the set
\begin{align*}
  \mathrm{Cov}_{Y}
  &:=
  \left\lbrace
      \mathbf{Open}_{Y}^{\mathrm{cov}_{Y}}
    \,
    \vert
    \,
      \mathrm{cov}_{Y}
      \text{ is an open cover generator of }
      Y
  \right\rbrace
\end{align*}
by
\begin{align*}
  \mathrm{cov}_{Y}^{\alpha}
  \leq_{\mathrm{Cov}_{Y}}
  \mathrm{cov}_{Y}
  \qquad
  &:\Leftrightarrow
  \qquad
  \mathrm{cov}_{Y}^{\alpha}
  \text{ is a refinement of }
  \mathrm{cov}_{Y}
\end{align*}
One can even show that
\begin{align*}
  \left(
    \mathrm{Cov}_{Y},
    \leq_{\mathrm{Cov}_{Y}}
  \right)
\end{align*}
is a directed set.
See \cite{273ba834} for these particular facts.
\item[$\bullet$]
Note that for a set $Y$, any subset $\mathfrak{S}_{Y} \subset \mathfrak{P}(Y)$ gives rise to a topology.
To this end, let us briefly explain what we mean by a basis and a subbasis of a topology.
For a space $(Y,\mathfrak{T}_{Y})$, a subset $\mathfrak{B}_{Y} \subset \mathfrak{T}_{Y}$ is called a \textbf{basis (for $\mathfrak{T}_{Y}$)} if any $U \in \mathfrak{T}_{Y}$ is the union of elements of $\mathfrak{B}_{Y}$, while a subset $\mathfrak{S}_{Y} \subset \mathfrak{T}_{Y}$ is called a \textbf{subbasis (for $\mathfrak{T}_{Y}$)} if all the finite intersections of elements of $\mathfrak{S}_{Y}$ form a basis for $\mathfrak{T}_{Y}$.
Note the convention we follow here: the empty intersection is by definition the whole space, while the empty union is the empty set.
So, any subset $\mathfrak{S}_{Y} \subset \mathfrak{P}(Y)$ yields a unique topology on $Y$ essentially by taking finite intersections and then arbitrary unions.
For more information on this, see \cite{273ba834}.
Note that taking the preimage of a function $f \colon Y_{1} \rightarrow Y_{2}$ preserves finite intersections and arbitrary unions, in the sense that
\begin{align*}
  f^{-1}
  \left(
    \bigcap_{k \in \mathbb{N}_{n}}
    U_{k}
  \right)
  &=
  \bigcap_{k \in \mathbb{N}_{n}}
  f^{-1}(U_{k})
  \\
  f^{-1}
  \left(
    \bigcup_{k \in K}
    U_{k}
  \right)
  &=
  \bigcup_{k \in K}
  f^{-1}(U_{k})
\end{align*}
Hence, it suffices to check the continuity of $f$ on a subbasis of $Y_{2}$.
\item[$\bullet$]
Assume we have topologies $\mathfrak{T}_{1}$ and $\mathfrak{T}_{2}$ on $Y$.
We call $\mathfrak{T}_{1}$ \textbf{coarser} than $\mathfrak{T}_{2}$, or equivalently, $\mathfrak{T}_{2}$ \textbf{finer} than $\mathfrak{T}_{1}$, if 
\begin{align*}
  \mathfrak{T}_{1}
  &\subset
  \mathfrak{T}_{2}
\end{align*}
In particular,
\begin{align*}
  \mathrm{id}_{Y}
  &\in
  \mathrm{mor}_{\mathbf{Top}}
  \left(
    (Y,\mathfrak{T}_{1}),
    (Y,\mathfrak{T}_{2})
  \right)
\end{align*}
is continuous if and only if $\mathfrak{T}_{2}$ is coarser than $\mathfrak{T}_{1}$.
\item[$\bullet$]
Let us look at two common sorts of topologies on a set $Y$ that frequently occur: the initial and terminal topologies.
To this end, fix a set $Y$ and a family of spaces
\begin{align*}
  s
  \colon
  K
  &\rightarrow
  \mathrm{ob}_{\mathbf{Top}}
\end{align*}
\\
Given functions
\begin{align*}
  f_{k}
  \colon
  Y
  &\rightarrow
  s(k)
\end{align*}
for all $k \in K$, we call the topology on $Y$ whose subbasis is made up of all the $f_{k}^{-1}(U)$ (with $U$ open in $s(k)$) the \textbf{initial topology (on $Y$ w.r.t. $k \mapsto f_{k}$)}.
This is the coarsest topology on $Y$ such that all $f_{k}$ are continuous.
\\
On the other hand, given functions
\begin{align*}
  f_{k}
  \colon
  s(k)
  &\rightarrow
  Y
\end{align*}
for all $k \in K$, we call the topology on $Y$ where $U \subset Y$ is open if and only if $f_{k}^{-1}(U)$ is open in $s(k)$ for all $k \in K$ the \textbf{terminal topology (on $Y$ w.r.t. $k \mapsto f_{k}$)}.
This is the finest topology on $Y$ such that all $f_{k}$ are continuous.
\item[$\bullet$]
It is also of interest in algebraic topology to equip a space with a specified, fixed base point.
This means a space $Y$ together with an element of that space.
So, let us call a $3$-tuple
\begin{align*}
  (Y,y)
  &\doteq
  (Y,\mathfrak{T}_{Y},y)
\end{align*}
a \textbf{pointed (topological) space} if $(Y,\mathfrak{T}_{Y})$ is a topological space and $y \in Y$.
If $(Y,y)$ is a pointed space, then $y$ is called the \textbf{base-point}.
Given pointed spaces $(Y_{1},y_{1})$, $(Y_{2},y_{2})$, a function $f \colon Y_{1} \rightarrow Y_{2}$ is called \textbf{base-point preserving} if $f(y_{1}) = y_{2}$.
The category corresponding to $\mathbf{Top}$ is denoted $\mathbf{Top}_{\ast}$; its objects are the pointed spaces, and its morphisms are the ones from $\mathbf{Top}$ that are base-point preserving.
$\mathbf{Top}_{\ast}$ is called the \textbf{category of pointed (small) topological spaces}.
\end{enumerate}
By the way, algebraic topology is, broadly speaking, about functors with domain $\mathbf{Top}$ or $\mathbf{Top}_{\ast}$ and whose codomain is a category derived from an algebraic structure (with $\mathbf{Grp}$ or $\mathbf{Ab}$ being the standard).
\\
As a last point, what we provide here are only the bare necessities of topology (let alone algebraic topology), without much intuition.
As a warning, don't underestimate that.
\end{exa}
\begin{prf}
Do it yourself.
But if you aren't familiar with topology, don't hesitate to consult some literature like \cite{273ba834} in the near future to get some familiarity with the subject.
\\
\phantom{proven}
\hfill
$\square$
\end{prf}
Note that just as $\mathbf{Top}$ is a category of spaces, there is also a category of {\glqq}smooth spaces{\grqq}.
Namely, we could define a category $\mathbf{Diff}_{\infty}$ whose objects are (small) smooth manifolds and whose morphisms are smooth functions between smooth manifolds.
We won't define what this means here, but rather refer the unfamiliar reader to \cite{797789bc}.
However, we will sometimes use $\mathbf{Diff}_{\infty}$, and hence we should give it a name.
$\mathbf{Diff}_{\infty}$ is called the \textbf{category of smooth manifolds}.
\\\\
Now back to the general theory.
Beyond isomorphisms of categories, let us describe a weaker notion of being quantitatively the same by defining full and faithful functors.
A functor $F_{\alpha\beta}$ is \textbf{full} if for all $X_{1}^{\alpha},X_{2}^{\alpha}$ and all
\begin{align*}
  f^{\beta}
  &\in
  \mathrm{mor}_{\mathbf{C}_{\beta}}
  (F_{\alpha\beta}(X_{1}^{\alpha}),F_{\alpha\beta}(X_{2}^{\alpha}))
\end{align*}
there is an $f_{12}^{\alpha}$ such that
\begin{align*}
  f^{\beta}
  &=
  F_{\alpha\beta}(f_{12}^{\alpha})
\end{align*}
The composition of full functors is evidently full.
A functor $F_{\alpha\beta}$ is \textbf{faithful} if for all $X_{1}^{\alpha},X_{2}^{\alpha}$ and all
\begin{align*}
  f^{\alpha},g^{\alpha}
  \in
  \mathrm{mor}_{\mathbf{C}_{\alpha}}(X_{1}^{\alpha},X_{2}^{\alpha})
\end{align*}
the implication
\begin{align*}
  F_{\alpha\beta}(f^{\alpha})
  =
  F_{\alpha\beta}(g^{\alpha})
  \qquad
  &\Rightarrow
  \qquad
  f^{\alpha}
  =
  g^{\alpha}
\end{align*}
is true.
Again, the composition of faithful functors is evidently faithful.
A functor is called \textbf{fully faithful} or equivalently an \textbf{embedding} if it is full and faithful.
The property full expresses the functor's surjectivity on the morphism sets, whereas faithful expresses injectivity on them.
Fully faithful then obviously means bijectivity.
All of this is clear from the definition of the corresponding properties.
The terminology embedding is particularly interesting.
In our context, this is just another word for a fully faithful functor.
Before spoiling too much, let's defer the explanation to the end of this subsection where the necessary statement is eventually available.
In fact, only then will we be in a position to really explain why fully faithful is a weaker - but in some sense, for category theory, sufficient - notion of being quantitatively the same.
Another particularly interesting case related in spirit to embeddings, at least, involves faithful functors $P$ from $\mathbf{C}$ to $\mathbf{Set}$, in which case we speak of a concrete category.
So, a \textbf{concrete category} is a tuple consisting of a category $\mathbf{C}$ and a faithful functor $P \colon \mathbf{C} \rightarrow \mathbf{Set}$.
So whenever $(\mathbf{C},P)$ is a concrete category, we can interpret the morphisms in $\mathbf{C}$ as functions between the sets associated with the objects in $\mathbf{C}$.
Composition is just the standard composition of functions.
You should absolutely compare this to the (C3) trick from remark \ref{rem:c3trick}.
In the end, we have a concrete idea of a potentially quite abstract category.
This suggests the notational convention to write $f_{12} \colon X_{1} \rightarrow X_{2}$ for a morphism.
Furthermore, we could informally draw a picture
\begin{align*}
  X_{1}
  \xrightarrow{f_{12}}
  X_{2}
\end{align*}
And consequently for a composition $f_{23} \circ f_{12}$
\begin{align*}
  X_{1}
  \xrightarrow{f_{23} \circ f_{12}}
  X_{3}
  \qquad
  &\text{or equivalently}
  \qquad
  X_{1}
  \xrightarrow{f_{12}}
  X_{2}
  \xrightarrow{f_{23}}
  X_{3}
\end{align*}
Hence, we can extend the notion of commutative diagrams of functions to morphisms.
In category theory, a commutative diagram is understood as a certain functor and is visualized as a generalization of the above.
A functor\footnote{note that some authors say diagram instead of functor} from the poset category of a partially ordered set to an arbitrary category is called a \textbf{commutative diagram}.
Visualization of a commutative diagram $D \colon \pmb{\leq}_{Y} \rightarrow \mathbf{C}$ is possible if $Y$ contains only, let's say, manageably - particularly finitely - many elements.
In fact, most often one is concerned with fewer than a dozen elements.
To visualize a formal commutative diagram $D \colon \pmb{\leq}_{Y} \rightarrow \mathbf{C}$, we provide the following meta-algorithm\footnote{an instruction understandable to a human} for drawing it:
\begin{description}
\item[Step 1]
Draw a unique symbol for the object $D(y)$ for all $y \in Y$.
\item[Step 2]
Let $y_{1},y_{2} \in Y$ be such that there is no $y \in Y$ satisfying $y_{1} \leq_{Y} y$ and $y \leq_{Y} y_{2}$.
Then draw an arrow labeled with a unique symbol for $D(y_{1},y_{2})$, starting at the symbol drawn for $D(y_{1})$ and ending at the symbol drawn for $D(y_{2})$, if $y_{1} \neq y_{2}$ and $y_{1} \leq_{Y} y_{2}$.
\end{description}
By saying that {\glqq}a diagram commutes{\grqq} w.r.t. the drawing from steps one and two, we mean that any two compositions of arrows with the same starting and ending points must be equal.
The algorithm is reversible in the sense that a visualization of a commutative diagram is sufficient to reconstruct the commutative diagram formally as a functor on a poset category.
As an example, we take the set $\mathbb{N}_{4}^{\times} = \lbrace 1,2,3,4 \rbrace$ with the partial order
\begin{align*}
  \leq_{\mathbb{N}_{4}^{\times}}
  &:=
  \lbrace
    (1,1),
    (2,2),
    (3,3),
    (4,4),
    (1,2),
    (1,3),
    (2,4),
    (3,4),
    (1,4)
  \rbrace
\end{align*}
and the commutative diagram $D \colon \pmb{\leq}_{\mathbb{N}_{4}^{\times}} \rightarrow \mathbf{C}$ drawn as follows:
\[
\begin{tikzcd}[sep=huge]
  D(1)
  &
  D(2)
  \\
  D(3)
  &
  D(4)
\end{tikzcd}
\qquad
\rightsquigarrow
\qquad
\begin{tikzcd}[sep=huge]
  D(1)
  \arrow{r}{D(1,2)}
  \arrow[swap]{d}{D(1,3)}
  &
  D(2)
  \arrow{d}{D(2,4)}
  \\
  D(3)
  \arrow{r}{D(3,4)}
  &
  D(4)
\end{tikzcd}
\]
To say that this drawing commutes means that
\begin{align*}
  D(3,4)
  \circ
  D(1,3)
  &=
  D(2,4)
  \circ
  D(1,2)
\end{align*}
After this graphical excursion, we come back to functors in general.
What we have said so far about functors suggests that one can view them as a kind of structure-preserving function between categories.
For small categories, we were able to make this perfectly precise in TG via the category $\mathbf{Cat}$.
Anyway, a nice property of functors illustrating this further is given by the following pretty important statement:
\\
\begin{thm}
\label{thm:catiso}
Let $F \colon \mathbf{C} \rightarrow \mathbf{C}_{\alpha}$ be a functor.
\begin{enumerate}
\item[(a)]
If $f_{12} \in \mathrm{mor}_{\mathbf{C}}(X_{1},X_{2})$ is an isomorphism, so is $F(f_{12})$.
\item[(b)]
If $F$ is an embedding, then $f_{12} \in \mathrm{mor}_{\mathbf{C}}(X_{1},X_{2})$ is an isomorphism if and only if $F(f_{12})$ is.
\end{enumerate}
\end{thm}
\begin{prf}
\begin{enumerate}
\item[(a)]
We have the equalities
\begin{align*}
  F(f_{12})
  \circ
  F(f_{12}^{-1})
  &=
  F(f_{12} \circ f_{12}^{-1})
  =
  F(\mathrm{id}_{X_{2}})
  =
  \mathrm{id}_{F(X_{2})}
  \\
  F(f_{12}^{-1})
  \circ
  F(f_{12})
  &=
  F(f_{12}^{-1} \circ f_{12})
  =
  F(\mathrm{id}_{X_{1}})
  =
  \mathrm{id}_{F(X_{1})}
\end{align*}
which prove the proposition.
\item[(b)]
Let $F(f_{12})$ be an isomorphism.
Since $F$ is full, there must be an $f_{21}$ such that the equalities
\begin{align*}
  \mathrm{id}_{F(X_{2})}
  &=
  F(f_{12})
  \circ
  F(f_{21})
  =
  F(f_{12} \circ f_{21})
  \\
  \mathrm{id}_{F(X_{1})}
  &=
  F(f_{21})
  \circ
  F(f_{12})
  =
  F(f_{21} \circ f_{12})
\end{align*}
hold.
Since $F$ is faithful, $\mathrm{id}_{X_{i}}$ is the only morphism that maps to $\mathrm{id}_{F(X_{i})}$ for $i = 1,2$.
Thus, we must have the equalities
\begin{align*}
  \mathrm{id}_{X_{2}}
  &=
  f_{12}
  \circ
  f_{21}
  \\
  \mathrm{id}_{X_{1}}
  &=
  f_{21}
  \circ
  f_{12}
\end{align*}
This, together with (a), proves the claim.
\end{enumerate}
\phantom{proven}
\hfill
$\square$
\end{prf}
The purpose of theorem \ref{thm:catiso} is, on the one hand, classification (part (a)).
Roughly speaking, a category represents a mathematical idea, and a functor relates two ideas.
Hence, a classification achieved in one subject provides a way to classify things in the other.
We want to emphasize here that part (a) of the theorem is often used in its negated form.
That is, using the notation from theorem \ref{thm:catiso}, non-isomorphic objects $F(X_{1})$ and $F(X_{2})$ imply non-isomorphic objects $X_{1}$ and $X_{2}$.
In algebraic topology particularly, this version is typically dominant.
On the other hand, from part (b), one can derive that if $F$ is an embedding, then $F$ is injective on objects up to isomorphism, that is:
\begin{align*}
  F(X_{1})
  \cong
  F(X_{2})
  \qquad
  &\Rightarrow
  \qquad
  X_{1}
  \cong
  X_{2}
\end{align*}
If we considered isomorphism to be good enough to replace equality, then embedding would be a good name.
In other words, this holds true in a structural set theory, or ultimately in UFP-HoTT.
We will return to this topic again and again to finally convince the reader that fully faithful is the most sensible concept for an embedding.
The keywords are: principle of equivalence, Yoneda functor, and topos embedding.
\\
Lastly, let us have a brief look at a certain kind of functor utilizing theorem \ref{thm:catiso}.
As we know from this subsection and the previous subsection \ref{sec:cat}, we can consider a group $(G,\cdot,\mathrm{id},\mathrm{inv})$ as a category $\mathbf{B}G$ with exactly one object and where every morphism is an isomorphism.
Then, for an arbitrary category $\mathbf{C}$, we call a functor $F_{G}$ from $\mathbf{B}G$ to $\mathbf{C}$ a \textbf{representation (of $G$ in $\mathbf{C}$)}.
In other words, a representation determines an object
\begin{align*}
  X
  &=
  F_{G}(\emptyset)
\end{align*}
where $\emptyset$ is the single object in $\mathbf{B}G$, and a function from
\begin{align*}
  G
  &=
  \mathrm{mor}_{\mathbf{B}G}(\emptyset,\emptyset)
\end{align*}
to $\mathrm{aut}_{\mathbf{C}}(X,X)$ due to theorem \ref{thm:catiso}.
This function is clearly a homomorphism.
Representations allow us to study group theory in a category $\mathbf{C}$, that is, in terms of a concept that might be better understood.
Most often, $\mathbf{C}$ is chosen to be some category of vector spaces.
