%\nocite{0d7b89ad}
%\nocite{66edf75b}
%\nocite{ea5d49bf}
%\nocite{0349e8ea}
%\nocite{2d5c2e63}
%\nocite{e5194763}
%\nocite{00000011}
For the record, in this subsection let
\begin{align*}
  n,
  n_{1},
  n_{2}
  \in
  \mathbb{N}
\end{align*}
while
\begin{align*}
  N,
  N_{1},
  N_{2}
  \in
  \mathbb{N}
  \cup
  \lbrace
    \infty
  \rbrace
\end{align*}
Furthermore, whenever we talk about $N$-groupoids and $N$-categories, we mean weak $N$-groupoids and weak $N$-categories, respectively.\footnote{note that $0$-groupoids and $0$-categories are just mere sets}
And if we do not mean weak, we will specify strict.
This is a common convention.
Lastly, let's agree to use $n$-morphism for both higher groupoids and higher categories; if we need to restrict to one of these cases, we'll say $n$-path for the higher groupoid case and $n$-arrow for the higher category case.
This is just a convenient convention here without too much intended meaning.
\\\\
Higher-level structures are informally understood as structures on higher-level sets, analogous to the structures on sets we informally introduced in remark \ref{rem:c3trick}.
The questions are:
\begin{enumerate}
\item[$\bullet$]
What is a higher-level set?
\item[$\bullet$]
What do higher-level sets have to do with category theory?
\end{enumerate}
Well, there are different ideas about what higher-level sets can be.
We take the stance here that a next-level set should be a set where any two elements are linked by arbitrarily many paths (for example, directed or undirected) that can be concatenated in arbitrary ways (where you have to respect the direction in the case of directed paths, of course).
More concisely, a next-level set should be a set plus a second set containing, for example, paths (or whatever) that structure the first set.
And we end up with two sets - or better yet, a $2$-dimensional set.
But be aware that we are not talking about ordinary undirected and directed graphs.
What we are talking about is nothing but pre-formal groupoid theory and category theory\footnote{categories in TG as we defined them are equivalent to something that in graph theory goes by the name of a \textit{directed multidigraph}}.
As we learned in subsection \ref{sec:nt}, we can structure a set of $1$-morphisms with $2$-morphisms in the same way we structured a set (of $0$-morphisms) with $1$-morphisms between elements to yield a weak $2$-groupoid or weak $2$-category, respectively.
In other words, a $3$-dimensional set.
Carrying on recursively in this manner, we end up with an $n+1$-dimensional set as either a weak $n$-groupoid or a weak $n$-category.
The modern idea is then to replace sets as the fundamental mathematical objects with weak $\infty$-groupoids or weak $\infty$-categories (or any other infinity version of a higher-level set you can think of) in a mathematical theory of everything.
\\
So now what? $n$-paths or $n$-arrows? There is a guy (\cite{e5194763}) who opposes the idea of pre-formal $n$-arrows here, arguing that undirected paths are more fundamental than directed ones, just as manifolds are more fundamental than oriented manifolds.
That is, a directed path in our sense would just be an undirected path with an additional directional structure.
However, he considers categories as a possibility for next-level sets, albeit in a different manner than we do here.
Yet, we can also argue for directed paths instead of undirected paths here, since one can consider directed paths to be equally (or even more) fundamental than undirected paths for the following reason: you can intuitively think of directed paths described by category theory as paths with a slope that can never be traversed uphill.
This is a synthetic description of directed paths, which contains ordinary (undirected) paths as the special case of horizontal paths.
To make this fully work geometrically for an arrow $f_{12} \colon X_{1} \rightarrow X_{2}$, we should draw the objects $X_{1},X_{2}$ as vertical straight lines and the arrows $f_{12}$ as areas filled with criss-cross lines that we are never allowed to follow uphill.
So if the arrow $f_{12}$ is an isomorphism we would draw
\[
\begin{tikzpicture}[scale=0.75]
  \filldraw[draw=white,pattern=horizontal lines]
    (-1,1)
    rectangle
    (1,5);
  \draw
    (-1,1)
    --
    (-1,5);
  \draw
    (1,1)
    --
    (1,5);
  \draw[->]
    (-1,0)
    -- node[above] {$f_{12}$}
    (1,0);
  \draw
    (-1,0) node[left] {$X_{1}$}
    --
    (-1,0);
  \draw
    (1,0)
    --
    (1,0) node[right] {$X_{2}$};
\end{tikzpicture}
\]
and otherwise
\[
\begin{tikzpicture}[scale=0.75]
  \filldraw[draw=white,pattern=north west lines]
    (-1,1)
    rectangle
    (1,5);
  \draw
    (-1,1)
    --
    (-1,5);
  \draw
    (1,1)
    --
    (1,5);
  \draw[->]
    (-1,0)
    -- node[above] {$f_{12}$}
    (1,0);
  \draw
    (-1,0) node[left] {$X_{1}$}
    --
    (-1,0);
  \draw
    (1,0)
    --
    (1,0) node[right] {$X_{2}$};
\end{tikzpicture}
\]
Hence, a groupoid would be the special case where all arrows are illustrated by areas filled with horizontal paths.
And, in fact, the guy in \cite{e5194763} concedes that philosophically, $1$-arrows as in our approach to category theory are also legit as basic mathematical objects and don't necessarily have to be considered $1$-paths with additional structure.
He even admits his line of argument is {\glqq}moot{\grqq} if somebody finds something like UFP-HoTT for directed paths.
That is, a formal synthetic theory of so-called {\glqq}directed homotopy theory{\grqq} - (synthetic) homotopy theory with directed $n$-paths, or $n$-arrows following our terminological convention - just as UFP-HoTT is (synthetic) homotopy theory with ordinary (undirected) $n$-paths.
But at the moment, UFP-HoTT is far more developed\footnote{indeed, it is mature enough to serve as a foundation of mathematics with basic mathematical objects $\infty$-groupoids} than any directed version of it.
This is another argument in \cite{e5194763}, which we recommend as lazy weekend literature for the interested reader.
By the way, the same author has written some quite worthwhile notes \cite{2d5c2e63} about intuition for homotopy type theory in a similar style, which we also highly recommend on this subject.
\\\\
Now, whatever we choose as a higher-level set - higher groupoids or higher categories - we deal with weak versions of them, and this suggests that equality should always mean equivalence when talking about $N$-dimensional sets.
This means (strict) equality on the $N$-th level and coherent isomorphism elsewhere, unless $N = \infty$, where it just means coherent isomorphism.
For sets this is equality, and for $2$-dimensional sets it is isomorphism on $0$-morphisms and equality on $1$-morphisms.
Note that if there were an $n+1$-st level, then strict equality on the $n$-th level would be identity.
UFP-HoTT has a pretty nice perspective on this: identity isomorphisms are no better than coherent isomorphisms; you just have to keep track of which coherent isomorphism you used to prove equivalence.
This is univalence, and it expresses that (strict) equality is expanded to equivalence.
The modern approach to avoiding this asymmetry of having both equality and isomorphism in the categorical context is to consider $(N_{1},N_{2})$-categories, which have arrows on all levels, but all $k$-arrows with $k > N_{1} \geq N_{2}$ are identities, and all $k$-arrows with $N_{1} \geq k > N_{2}$ are invertible.
Equivalence is then just coherent isomorphism.
In this setting, $N$-categories are $(N,N)$-categories.
$(N_{1},N_{2})$-categories are hybrids of $\infty$-groupoids and $\infty$-categories, and they might be used to find an $\infty$-category generalization of UFP-HoTT, where progress is being made in the $(\infty,1)$-category case.
$(\infty,1)$-categories are well-understood.
You can imagine these as ordinary categories where the morphism sets are not just $1$-dimensional sets, but $\infty$-groupoids, which is to say homotopy types per the Grothendieck hypothesis \ref{prp:groth}.
This is needed when doing homotopy theory.\footnote{just think of fiber sequences in $\mathbf{Top}$, for example, where one has to topologize some morphism sets to make things work out} So, $(\infty,1)$-categories provide a basic setting for doing homotopy theory.
But we can't expect this to suffice, just as we couldn't expect set theory to work equally well in any category.
There, we found topos theory, which provides a setting to do reasonable set theory.
Therefore, we would expect a sensible notion of $(\infty,1)$-topoi to be a setting for homotopy theory, in that the objects of an $(\infty,1)$-topos behave like homotopy types.
This is, in fact, the case.
However, we can't elaborate further on that, since we lack model categories as a $(1,1)$-categorical formulation of homotopy theory on the one hand, and a formal definition of $(\infty,1)$-categories on the other.
Moreover, we lack some categorical ideas from later sections - fibrations (section \ref{sec:fibration}) and simplicial sets (section \ref{sec:sset}) - which are usually utilized in the formal definitions we would need.
But let's go ahead and refer to \cite{0349e8ea} if you want to formally understand these things.
In particular, $(\infty,1)$-topos theory, as the title of \cite{0349e8ea} suggests.
\cite{0349e8ea} seems to be the undisputed standard reference on $(\infty,1)$-topos theory.
The internal language of $(\infty,1)$-topoi seems to be homotopy type theory.
In conclusion, let's just say that an $(\infty,1)$-topos is a place where you can do homotopy theory.
\\
While we are on the topic of Lurie's work anyway, a historical remark: one of the main reasons to prefer $(N,N)$-categories over weak $N$-categories is that there are problems proving the so-called cobordism hypothesis due to Baez for the latter, but Lurie proved it in the case of $(\infty,N)$-categories.
For more on this, see \cite{ea5d49bf} and \cite{00000011}.
\\\\
Now that we have an idea of what higher-level sets should be, we turn to the question of how we can transfer structures on $N_{1}$-dimensional sets to corresponding structures on $N_{2}$-dimensional sets.\footnote{a $0$-dimensional set can be seen as the truth values {\glqq}true{\grqq} and {\glqq}false{\grqq}}
In particular, if we are given a method to transfer some sorts of structures from $N_{1}$-dimensional sets to corresponding structures on $N_{2}$-dimensional sets, then if the method is applied to a mere\footnote{without structure} $N_{1}$-dimensional set, it should yield an $N_{2}$-dimensional set.
This is a minimal condition for any sensible method, and if it holds for the case $n_{2} = n_{1} + 1$ for all $n_{1},n_{2}$, we can construct - and hence define - $n$-dimensional sets for all $n$ via such a method.
\\
However, this isn't directly applicable for getting $\infty$-dimensional sets, so you have to rely on other methods.
To get $\infty$-groupoids in UFP-HoTT, for example, the types are characterized by deductive steps that make all types behave like $\infty$-groupoids - or more intuitively, spaces.
$n$-groupoids, or rather, $n$-types, are then defined as the $\infty$-groupoids with only identities above level $n$.
This allows us to construct the $n+1$-groupoid/type of $n$-groupoids/types of some (univalent) universe\footnote{the idea is the same as for Grothendieck universes though UFP-HoTT uses Russell-style universes} $\mathcal{U}$ of types/$\infty$-groupoids as a subtype via a so-called dependent sum\footnote{something like a collection of ordered pairs where the second coordinate depends on the first} where the first coordinate is an inhabitant of the universe and the second is a proof that this inhabitant is an $n$-groupoid/type.
As a formula, this looks like
\begin{align*}
  n\textrm{-Type}
  \doteq
  n\textrm{-Type}_{\mathcal{U}}
  &:=
  \sum_{T \colon \mathcal{U}}
  \textrm{is-}n\textrm{-type}(T)
\end{align*}
Let's agree that $\infty\textrm{-Type}_{\mathcal{U}}$ is just $\mathcal{U}$.
Moreover, there are rules for how to make the higher-groupoid structure of any $\infty$-groupoid trivial above some level $n$ to yield an $n$-groupoid.
This is called $n$-truncation and corresponds to the $n$-th Postnikov section in classical homotopy theory with ordinary topological spaces.
But unlike Postnikov towers in the classical sense, $n$-truncation is formally built into UFP-HoTT.
This is an important feature of UFP-HoTT.
We could now hope to transfer higher-level structures via $n$-truncation.
Namely, assume a type $T$ and an $n$-type $T_{n}$ that includes some known structure; that is, the structure is part of the types.
Then, if $T_{n}$ is the $n$-truncation of $T$ and if the $n$-truncation has a right inverse - or better yet, is a section - then we would consider $T$ to be a type with a structure of the same sort as the structure on $T_{n}$.
Note that $T$ can be a groupoid of any dimension and is not necessarily a non-trivial $\infty$-groupoid.
But usually, the dimension of $T$ is higher than $n$.
We don't want to dig any deeper at this point, but rather turn to a process similar in spirit that also works very well.
One might call it weak internalization:
\begin{description}
\item[Step 1]
define a structure on an inhabitant of $N\textrm{-Type}$ as something internal to $N\textrm{-Type}$ for some $N$
\item[Step 2]
try to use this internal definition for any $N$
\end{description}
For example, one can define a (weak) $\infty$-group to be a (weak) group object of $\mathcal{U}$; then a weak $N$-group is a (weak) group object of the type of $N\textrm{-Type}_{\mathcal{U}}$.
If you don't understand this yet, you will after reading UFP-HoTT.
But it's not too important for what follows.
\\
You can think of similar ideas for $\infty$-categories, assuming we even have a serious definition of them at all.\footnote{at best a generalization of UFP-HoTT in the sense of a synthetic theory of directed homotopy theory}
One can then again think of something like the $(n+1,n+1)$-category of $(n,n)$-categories ${}_{(n,n)}\mathbf{Cat}_{\mathcal{U}}$, where we agree to regard ${}_{(\infty,\infty)}\mathbf{Cat}_{\mathcal{U}}$ as a universe of $\infty$-categories.
We can then hope to find an $n$-truncation that truncates an $\infty$-category to an $(n,n)$-category by making all arrows above level $n$ trivial.
Hence, we can hope to transfer higher-level structures via $n$-truncation, just like in the higher groupoid case.
Note that with $(\infty,n)$-categories we have a hybrid of $\infty$-groupoids and $\infty$-categories, which suggests a weaker form of $n$-truncation where an $\infty$-category is $n$-truncated to an $(\infty,n)$-category by discarding all non-invertible arrows above level $n$.
However, this shouldn't concern us here, since the stronger notion is the one that corresponds to $n$-truncation in UFP-HoTT.
And transferring higher-level structures via this strong $n$-truncation applies.
In this way, you can, for example, transfer the structure of natural numbers on a set to the $1$-categorical context, yielding $\mathbf{Finset}$.
On the other hand, it is straightforward to generalize the idea of weak internalization as:
\begin{description}
\item[Step 1]
define a structure on an $N$-category as something internal to ${}_{(n,n)}\mathbf{Cat}$
\item[Step 2]
try to use this internal definition for any $N$
\end{description}
In subsection \ref{sec:internaliz}, we got a taste of the importance of internalization.
So it is no surprise that weak internalization is at least as important: it is at least as good as internalization, since it is internalization in the $(\infty,1)$-categorical context, which is a generalization of category theory.
\\\\
If we're honest, the most likely case you'll encounter in practice is having a structure on a set and wanting to make sense of it in the $2$-dimensional set case.
Ideally, you'd hope this process is recursive and translates into a way to go from $n$ to $n+1$.
Hence, we want to generalize a structure on a set to a structure on a category, or more generally, from the $n$ case to the $n+1$ case via a mostly informal algorithm that tells us how to do so.
In the following, we discuss two such ideas: (recursive) categorification\footnote{some people call it vertical categorification} and (recursive) oidification\footnote{some people call it horizontal categorification}.\footnote{the word recursive is not part of the standard terminology, but we find it less confusing at this point, since transferring higher-level structures via $n$-truncation and weak internalization are also considered a kind of categorification where we avoid the terminology as well}
\\
But let's first reconsider how the dimension terminology of higher-level sets emerges if we want $n+1$-dimensional sets to be $n$-categories.
What we mean is that a set is just an unstructured collection, but a category $\mathbf{C}$ consists essentially of a set of objects $\mathrm{ob}_{\mathbf{C}}$ and a set of arrows $\mathrm{Mor}_{\mathbf{C}}$ (governed by composition) - a $2$-tuple - while a $3$-category consists of a set of $0$-arrows (objects), a set of $1$-arrows (morphisms), and a set of $2$-arrows (governed by two kinds of composition: vertical and horizontal) - a $3$-tuple.
This process extends to an arbitrary $n$ (provided we have a definition of an $n$-category).
These $n$-tuples are what we mean when we say a set of dimension $n$.
Moreover, note that a functor is a $2$-dimensional function in this sense, since it essentially consists of two functions: one on objects and one on morphisms.
And an $N$-functor between $N$-categories should be a collection of functions $f_{n^{\backprime}}$ where $n^{\backprime} \in \mathbb{N}_{N}$, such that $f_{n^{\backprime}}$ maps $n^{\backprime}$-morphisms to $n^{\backprime}$-morphisms respecting the various compositions and identities in a weak way, that is, up to equivalence.\footnote{one also gets coherence conditions for $n$-functors}
Moreover, note that a natural transformation is a function mapping $0$-morphisms to $1$-morphisms respecting the functor application.\footnote{it doesn't matter if we first apply the functor and then transform or the other way around}
In the $N$-category case, this suggests considering $N$-functors and $N$-natural transformations as special cases of a more general notion called a transfor\footnote{a made-up word from functor and natural transformation}.
Let $n_{0} \in \mathbb{N}_{N}^{\times}$.
Then, if an $(N,n_{0}-1)$-transfor is defined, an $(N,n_{0})$-transfor should be a family of functions indexed by $n^{\backprime} \leq N - n_{0}$ mapping $n^{\backprime}$-morphisms to $n^{\backprime}+n_{0}$-morphisms respecting $(N,n_{0}-1)$-transfor application up to equivalence, where the $(N,0)$-transfor case should just be an $N$-functor.
$(N,1)$-transfors would then be $N$-natural transformations.
Let's illustrate this a bit for $N \neq \infty$.
If
\[
\begin{tikzcd}[sep=tiny]
  {}_{0}\mathrm{Mor}_{\mathbf{W}}
  \\
  \vdots
  \\
  {}_{n}\mathrm{Mor}_{\mathbf{W}}
\end{tikzcd}
\]
illustrates an $n$-category $\mathbf{W}$, then for $n$-categories $\mathbf{W}_{1}$ and $\mathbf{W}_{2}$ we can illustrate an $(n,n_{0})$-transfor for $n-n_{0}$ large enough as
\[
\begin{tikzcd}[row sep=tiny,column sep=large]
  {}_{0}\mathrm{Mor}_{\mathbf{W}_{1}}
  \arrow{rdd}{}
  &
  {}_{0}\mathrm{Mor}_{\mathbf{W}_{2}}
  \\
  \vdots
  &
  \vdots
  \\
  {}_{n_{0}}\mathrm{Mor}_{\mathbf{W}_{1}}
  \arrow{rdd}{}
  &
  {}_{n_{0}}\mathrm{Mor}_{\mathbf{W}_{2}}
  \\
  \vdots
  &
  \vdots
  \\
  \vdots
  &
  {}_{n_{0}+n_{0}}\mathrm{Mor}_{\mathbf{W}_{2}}
  \\
  \vdots
  &
  \vdots
  \\
  {}_{n-n_{0}}\mathrm{Mor}_{\mathbf{W}_{1}}
  \arrow{rdd}{}
  &
  \vdots
  \\
  \vdots
  &
  \vdots
  \\
  {}_{n}\mathrm{Mor}_{\mathbf{W}_{1}}
  &
  {}_{n}\mathrm{Mor}_{\mathbf{W}_{2}}
\end{tikzcd}
\]
The up to equivalence part cannot be illustrated here in generality.
The coherence laws are way too complicated for us here.
But we saw a special case in subsection \ref{sec:nt}, and we will see some more in subsubsection \ref{sec:hlm}.
\\
We now come to categorification and oidification.
\begin{enumerate}
\item[(RC)]
Categorification is the following, mostly informal process so far: for all $n$, when given a bunch of $n$-categories and a bunch of $(n,n_{0})$-transfors for all $0 \leq n_{0} \leq n$ subjected to some conditions only involving the $n$-categories and $(n,n_{0})$-transfors - this can be seen as a structure on these $n$-categories - then by replacing
\begin{description}
\item[Step 1]
each $n$-category with an $n+1$-category
\item[Step 2]
each $(n,n_{0})$-transfor with a suitable $(n+1,n_{0})$-transfor
\end{description}
we have categorified the structure to $n+1$-categories.
A more thorough discussion of this is given in \cite{66edf75b}.
Let's emphasize what this means when categorifying a set: given a bunch of sets and a bunch of functions with both domains and codomains involving only these sets, subjected to some conditions involving only these sets and functions, we can then replace each set with a category and each function with a suitable functor (the $(1,0)$-transfors).
In particular, an equality of sets must be replaced by equivalence (which actually should have already been done earlier) and equality of functions by equivalence (the $(1,1)$-transfors up to coherent isomorphism).
\\
An example is categorifying a monoid $(M,\cdot,\mathrm{id})$.
We replace $M$ with a category $\mathbf{C}$, $\cdot$ with a functor from $\mathbf{C} \times \mathbf{C}$ to $\mathbf{C}$, and $\mathrm{id}$ with a functor from $\mathbf{1}_{M}$ to $\mathbf{C}$, which, due to the terminality of $\mathbf{1}_{M}$ in $\mathbf{Cat}$, is nothing but an object $1$ of $\mathbf{C}$.
In the monoid properties (M1) and (M2), we replace $=$ with a natural isomorphism.
Then you have to look at the result to see what's missing to make it a sensible concept.
We do this in subsubsection \ref{sec:hlm} and categorify a monoid into a monoidal category.
An interesting peculiarity is that you can internalize monoids in monoidal categories.
This is a further idea called the microcosm principle, coined by Baez and Dolan in \cite{0d7b89ad}, where they give a definition of a weak $n$-category and prove a version of the microcosm principle which says that when we categorify a structure, we can internalize this structure there.
Even though, as already mentioned, weak $n$-categories aren't used much anymore due to their drawbacks, the paper \cite{0d7b89ad} is seminal for higher categories and still provides great intuition.
So we highly recommend reading it.
\item[(RO)]
Actually, we've already quietly introduced the informal meta-idea of oidification through two examples earlier in the notes.
Namely, the oidification of a monoid is a category, while the oidification of a group is a groupoid.
The process in these cases was that we had a structure on a set (monoid and group) and could show that it is equivalent to a certain kind of category (an ordinary category and a category with only isomorphisms, respectively) with exactly one object.
Then we allowed this kind of category to contain arbitrarily many objects to complete the oidification of the structure on a set.
So oidification in higher category theory should be very much like categorification: take a structure on an $n$-category and transfer it to the next level.
Hence, oidification is described by the following meta-algorithm: given some structure on an $n$-category for some $n \in \mathbb{N}$, then
\begin{description}
\item[Step 1]
show that the structure on this $n$-category is equivalent to a certain kind of $n+1$-category with precisely one $0$-morphism
\item[Step 2]
oidify by passing to this certain kind of $n+1$-category but allow arbitrarily many $0$-morphisms
\end{description}
\end{enumerate}
In the end, you might recognize that recursive categorification and oidification also let you go from a finite $n$ directly to $\infty$ after all.
That it is presented recursively is arguably for historical reasons.
\\\\
All in all, this subsection suggests that the $\infty$-version of a structure is more fundamental than any finite version, in the sense that the $\infty$-dimensional sets are the basic mathematical objects rather than just ordinary sets.
\\
The following subsection applies many of the ideas sketched here to the case of monoids, yielding mostly formal definitions.
