%\nocite{66edf75b}
%\nocite{0349e8ea}
%\nocite{7a40623d}
%\nocite{00000011}
In this section, we want to motivate how to generalize the idea of \textit{axiomatic cohomology} to the context of $(\infty,1)$-categories - that is, to categories up to coherent isomorphism where the {\glqq}morphism sets{\grqq} behave as $\infty$-groupoids.\footnote{Note that this is essentially to say we weakly enrich over a category of $\infty$-groupoids or topological spaces, or something.}
The Brown representability theorem for $\Omega$-spectra, discussed in example \ref{exa:loopradjoint}, suggests considering axiomatic cohomology as a special case of homotopy theory.
And this is what we'll exploit in the following.
In particular, we explain how to include the idea of characteristic classes, which allow us to examine the {\glqq}twists{\grqq} of a principal bundle (and hence instantons).
\\\\
First, we want to remind the reader of example \ref{exa:loopradjoint} regarding the loop space functor $\Omega$.
Loop spaces are of great interest in homotopy theory.
Besides defining homotopy groups in terms of loop spaces, there is an interesting theorem in \cite{8b5861fc} - proposition 4.66 - which ultimately leads to a fascinating hypothesis in higher category theory.
It states that the fiber $p^{-1}(b)$ (for some $b \in B$) of a fibration $p \colon E \rightarrow B$ is (weakly) homotopy equivalent to the loop space $\Omega(B)$ of $B$ if $E$ is contractible.
Now, since principal $G$-bundles with a topological group $G$ as structure group are specifically fibrations for sufficiently nice base spaces $B$ (particularly CW complexes, which is all we are interested in), one gets
\begin{align*}
  G
  &\cong
  \Omega(\mathrm{B}G)
\end{align*}
in $\mathbf{HTop}$.
This is why one calls the classifying space $\mathrm{B}G$ the delooping of $G$.
More generally, assume a category $\mathbf{C}$ with a terminal object $1_{\mathbf{C}}$.
Then, for an object $X$, an object $\mathrm{B}X \in \mathrm{ob}_{\mathbf{C}}$ together with a global element $e \colon 1_{\mathbf{C}} \rightarrow \mathrm{B}X$ is called the \textbf{delooping (of $X$)} if it is the unique (up to equivalence) such pair with the property that $X$ is isomorphic to the so-called \textit{loop space object of $\mathrm{B}X$}.
The loop space object is a certain homotopy pullback.
We didn't define homotopy pullbacks, but it is essentially a pullback up to homotopy in a category that allows for a bit of homotopy theory.
So, the loop space object of an object $X_{0}$ together with a global element $e_{0} \colon 1_{\mathbf{C}} \rightarrow X_{0}$ is the pullback of $e_{0}$ along itself, but commutativity is only up to homotopy in the appropriate sense.
For a global element $e_{0}$ in $\mathbf{Top}$, we get precisely the loops with base point $e_{0}(1_{\mathbf{Top}})$.
If you are curious, we suggest learning more about homotopy limits in \cite{7a40623d}, for example.
You could also look into the delooping hypothesis, which roughly links monoidal categories (see subsubsection \ref{sec:hlm} in chapter \ref{chap:cattg}) and their higher analogs in higher category theory.
For this, we refer you to \cite{00000011}.
You can additionally look at \cite{66edf75b}.
\\
Now, let us look at a very special $\Omega$-spectrum in this context.
Assume a group $G$ and $n \in \mathbb{N}^{\times}$.
A CW complex $K(G,n)$ is called an \textbf{Eilenberg-Mac Lane space for $(G,n)$} if
\begin{align*}
  \pi_{k}(K(G,n))
  &=
  \begin{cases}
    G
    &
    \text{if }
    k
    =
    n
    \\
    1_{\mathbf{Grp}}
    &
    \text{else}
  \end{cases}
\end{align*}
One can show that
\begin{align*}
  K(G,\cdot)
  \colon
  \mathbb{Z}
  &\rightarrow
  \mathbf{HTop}_{\ast}^{\textrm{CW}}
  \\
  n
  &\mapsto
  \begin{cases}
    K(G,n)
    &
    \text{if }
    n
    \geq
    1
    \\
    \Omega^{-n+1}(K(G,1))
    &
    \text{else}
  \end{cases}
\end{align*}
defines an $\Omega$-spectrum if $\Omega^{n}$ denotes the $n$-fold application of the loop space functor $\Omega$.\footnote{See \cite{8b5861fc} for this fact.} This means that
\begin{align*}
  K(G,0)
  &\cong
  \Omega^{n}(K(G,n))
\end{align*}
for all $n \in \mathbb{N}^{\times}$ and hence suggests considering $K(G,n)$ as the $n$-fold delooping of $K(G,0)$, written $\mathrm{B}^{n}K(G,0)$ for $n \in \mathbb{N}$.
In section \ref{sec:sset} of chapter \ref{chap:cattg}, we constructed $K(G,1)$ as a classifying space for discrete topological groups - that is, topological groups where the topology is the power set of the group.
But then the loop space of $K(G,1)$, which is $K(G,0)$, is just the discrete space $G$.
So
\begin{align*}
  G
  &\cong
  K(G,0)
\end{align*}
with $G$ considered as a discrete topological space.
After all, for an abelian group $G$, we get that
\begin{align*}
  h_{G}^{n}(X)
  &=
  \mathrm{hom}_{\mathbf{HTop}_{\ast}^{\textrm{CW}}}
  \left(
    X,
    \mathrm{B}^{n}G
  \right)
\end{align*}
is the $n$-th reduced singular cohomology for a CW complex $X$ with coefficients in $G$ for $n \in \mathbb{N}$.\footnote{This fact is also proved in \cite{8b5861fc}.} Let us briefly demonstrate that this makes sense by considering the example $n = 0$.
A full discussion, along with a pretty nice motivation for cohomology, can be found - although scattered through the text - in \cite{8b5861fc}.
\begin{enumerate}
\item[$\bullet$]
A $0$-cochain in the singular cohomology for $X$ with coefficients in $G$ is just a morphism $\phi$ in $\mathbf{Set}$ from $X$ to $G$.
To make this $0$-cochain $\phi$ into a $0$-cocycle, we must demand that $\phi$ is constant on the path components of $X$.
So, $0$-cocycles are precisely the continuous functions from $X$ to $G$ when $G$ is regarded as a discrete space.
The only $0$-coboundary is the constant function
\begin{align*}
  \phi_{e_{G}}
  \colon
  X
  &\rightarrow
  G
  \\
  x
  &\mapsto
  e_{G}
\end{align*}
where $e_{G}$ denotes the identity element of $G$.
So, for unreduced singular cohomology, the $0$-cocycles are already the degree-$0$ singular cohomology classes.
However, $0$-cocycles also correspond to the homotopy classes of continuous functions from $X$ to $G$, since $G$ is discrete and the only homotopies are the ones from $\phi$ to $\phi$, which are constant.
That is to say, they are defined by adding $\phi_{e_{G}}$.
\\
Now, for the reduced case, one has to divide out the constant\footnote{overall, and not only on path components} functions on $X$ with codomain $G$ from the $0$-cocycles above, since these are the $0$-coboundaries in the reduced case.
Note that for any $0$-cocycle $\phi$, there is a $g \in G$ such that $\phi + \phi_{g}$ - here $\phi_{g}$ denotes the constant function on $X$ with target $g$ and is thus a $0$-coboundary in the reduced case - is a basepoint-preserving continuous function from $X$ to $G$.
Hence, the reduced degree-$0$ singular cohomology classes correspond precisely to the basepoint-preserving continuous functions from $X$ to $G$, since the $0$-cocycles are constant on path components and are always cohomologous to a basepoint-preserving one.
Reduced degree-$0$ singular cohomology classes then also correspond to the homotopy classes of basepoint-preserving continuous functions from $X$ to $G$, since $G$ is discrete.
Also in this case, the only homotopies are the constant ones defined by $\phi_{e_{G}}$, but they no longer correspond to the reduced $0$-coboundaries.
This is because neither the reduced $0$-cocycles nor the reduced $0$-coboundaries are required to be basepoint-preserving.
So perhaps we could argue that we are using the wrong chain complex here, in the sense that it does not take basepoints into account.
\end{enumerate}
In the end, this special case shows explicitly that
\begin{align*}
  \mathrm{hom}_{\mathbf{HTop}_{\ast}^{\textrm{CW}}}
  \left(
    X,
    G
  \right)
\end{align*}
is precisely the $0$-th reduced singular cohomology for a CW complex $X$ with coefficients in an abelian group $G$.
Moreover, it supports the idea that it might be more sensible to consider the elements of
\begin{align*}
  \mathrm{hom}_{\mathbf{Top}_{\ast}^{\textrm{CW}}}
  \left(
    X,
    G
  \right)
\end{align*}
as $0$-cocycles, and a homotopy between such elements as a $0$-coboundary.
This idea directly suggests also considering
\begin{align*}
  \mathrm{hom}_{\mathbf{Top}_{\ast}^{\textrm{CW}}}
  \left(
    X,
    \mathrm{B}^{n}G
  \right)
\end{align*}
as $n$-cocycles and homotopies between such $n$-cocycles as $n$-coboundaries.
And if this is reasonable, then why cut off the homotopy information at all?
Just imagine the $(\infty,1)$-topos ${}_{(\infty,1)}\mathbf{Top}_{\ast}^{\textrm{CW}}$ where the objects are CW complexes with a basepoint, and the $1$-morphisms are basepoint-preserving continuous maps between CW complexes $X_{1}, X_{2}$, regarded as an $\infty$-groupoid denoted
\begin{align*}
  {}_{(\infty,1)}\mathbf{Top}_{\ast}^{\textrm{CW}}(X_{1},X_{2})
\end{align*}
Clearly, $K(G,0)$ (with a basepoint) is an object of ${}_{(\infty,1)}\mathbf{Top}_{\ast}^{\textrm{CW}}$, and for all CW complexes $X$, the $0$-truncation of
\begin{align*}
  {}_{(\infty,1)}\mathbf{Top}_{\ast}^{\textrm{CW}}
  \left(
    X,
    \mathrm{B}^{n}G
  \right)
\end{align*}
or, by using the homotopy hypothesis \ref{prp:groth}, the zero-th homotopy group\footnote{the path components} $\pi_{0}$ of this $\infty$-groupoid as a topological space is precisely the $n$-th reduced singular cohomology for a CW complex $X$ with coefficients in $G$ for $n \in \mathbb{N}$.
But instead of the $0$-truncation, we can also look at $n$-truncations for $n \in \mathbb{N}$ to get more interesting (homotopy) information, or even at the $\infty$-groupoid
\begin{align*}
  {}_{(\infty,1)}\mathbf{Top}_{\ast}^{\textrm{CW}}
  \left(
    X,
    \mathrm{B}^{n}G
  \right)
\end{align*}
to get all the homotopy information.
For instance, we have pointed out that $h_{G}^{1}(X)$ classifies isomorphism classes of principal $G$-bundles.
But this misses the physically crucial information of local symmetry needed for the principle of locality, and we said that we need
\begin{align*}
  {}_{(\infty,1)}\mathbf{Top}_{\ast}^{\textrm{CW}}
  \left(
    X,
    \mathrm{B}^{1}G
  \right)
\end{align*}
for a classification containing this information.
\\
At this point, there is also a way to generalize \textit{characteristic classes} measuring the non-triviality of principal $G$-bundles.
Characteristic classes are natural transformations from $\mathcal{P}_{G}$ (see example \ref{thm:repofbundlefunc}) to the functor $h_{\mathbb{Z}}^{\ast}$ consisting of all the $h_{\mathbb{Z}}^{n}$ in an appropriate way\footnote{The keyword is cohomology as a graded ring (see e.g., \cite{8b5861fc}) and forgetting the abelian group structure.}.
Namely any $G$-principal bundle over $X$ is the pullback $f^{\ast}\pi$ of the universal bundle $\pi \colon \mathrm{E}G \rightarrow \mathrm{B}G$ along a suitable $f \colon X \rightarrow \mathrm{B}G$.
So, the naturality of a characteristic class $\mathsf{C}$ is determined by
\begin{align*}
  \mathsf{C}(X)
  \left(
    [f^{\ast}\pi]
  \right)
  &=
  h_{\mathbb{Z}}^{\ast}(f)
  \circ
  \mathsf{C}(\mathrm{B}G)(\pi)
\end{align*}
But $\mathsf{C}(\mathrm{B}G)(\pi)$ is just a sequence of classes
\begin{align*}
  [c_{n}]
  &\in
  \mathrm{hom}_{\mathbf{HTop}_{\ast}^{\textrm{CW}}}
  \left(
    \mathrm{B}G,
    \mathrm{B}^{n}\mathbb{Z}
  \right)
\end{align*}
and composing with $h_{\mathbb{Z}}^{\ast}(f)$ is thus just a sequence of homotopy classes of $c_{n}$ precomposed with $f$.
Hence, the sequence determined by
\begin{align*}
  [c_{n} \circ f]
\end{align*}
must be
\begin{align*}
  \mathsf{C}(X)
  \left(
    [f^{\ast}\pi]
  \right)
\end{align*}
and encodes the twisting information of the bundles in $[f^{\ast}\pi]$.
So, we are tempted to say that a characteristic class of a cocycle is just the homotopy class of its precomposition with some cocycle.
One could argue that we always have to take all the deloopings into account at this point.
But we don't care about that here, since it is not our main focus.
\\\\
The nice thing about what we have said so far is that it essentially makes sense in any $(\infty,1)$-topos - and even any $(\infty,1)$-category.
Both are well-developed and formalized parts of higher category theory, e.g., in \cite{0349e8ea}.
In fact, Lurie's higher topos theory \cite{0349e8ea} begins with the classification of principal bundles by cohomology.
Anyways, let's give a definition of cohomology in this general setting.
\\
Assume an $(\infty,1)$-category ${}_{(\infty,1)}\mathbf{C}$ and objects $X$ and $A$ in ${}_{(\infty,1)}\mathbf{C}$.
Moreover, denote the $\infty$-groupoid of morphisms from $X$ to $A$ as
\begin{align*}
  {}_{(\infty,1)}\mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
and its $0$-truncation\footnote{This is generally the morphism set of the homotopy category of ${}_{(\infty,1)}\mathbf{C}$, in analogy to $\mathbf{HTop}$ for $\mathbf{Top}$.} as
\begin{align*}
  \pi_{0}
  \mathbf{C}
  \left(
    X,
    A
  \right)
  &\doteq
  \mathrm{mor}_{\mathrm{Ho}({}_{(\infty,1)}\mathbf{C})}
  \left(
    X,
    A
  \right)
\end{align*}
\begin{enumerate}
\item[$\bullet$]
The $\infty$-groupoid of morphisms
\begin{align*}
  {}_{(\infty,1)}\mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
is called the \textbf{($A$-)cohomology (of $X$)}, or equivalently, the \textbf{(degree-$0$) cohomology (of $X$ with coefficients in $A$)}.
An object of the $\infty$-groupoid of morphisms
\begin{align*}
  {}_{(\infty,1)}\mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
that is, a $1$-morphism in ${}_{(\infty,1)}\mathbf{C}$ from $X$ to $A$, is called a \textbf{cocycle (on $X$ with coefficients in $A$)}.
\item[$\bullet$]
A ($1$-)path of the $\infty$-groupoid
\begin{align*}
  {}_{(\infty,1)}\mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
is called a \textbf{coboundary (on $X$ with coefficients in $A$)}.
Moreover, given cocycles $\phi_{1}, \phi_{2}$ on $X$ with coefficients in $A$, we say $\phi_{1}$ is \textbf{cohomologous} to $\phi_{2}$, or equivalently, $\phi_{1}$ and $\phi_{2}$ are \textbf{cohomologous}, if there is a ($1$-)path from $\phi_{1}$ to $\phi_{2}$ in
\begin{align*}
  {}_{(\infty,1)}\mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
\item[$\bullet$]
The set
\begin{align*}
  \pi_{0}
  \mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
is called the \textbf{($A$-)cohomology set (of $X$)}, or equivalently, the \textbf{(degree-$0$) cohomology set (of $X$ with coefficients in $A$)}, while an element of
\begin{align*}
  \pi_{0}
  \mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
is called an \textbf{($A$-)cohomology class (on $X$)}.
Moreover, assume a cocycle $\phi$ on $X$ with coefficients in $A$.
Then we call its homotopy class
\begin{align*}
  [\phi]
  &\in
  \pi_{0}
  \mathbf{C}
  \left(
    X,
    A
  \right)
\end{align*}
the \textbf{($A$-)cohomology class (of $\phi$)}.
\item[$\bullet$]
Assume objects $A_{1}, A_{2}$ in ${}_{(\infty,1)}\mathbf{C}$.
Moreover, assume a cocycle $\phi$ on $X$ with coefficients in $A_{1}$ and a cocycle $c$ on $A_{1}$ with coefficients in $A_{2}$ - that is, morphisms $\phi$ from $X$ to $A_{1}$ and $c$ from $A_{1}$ to $A_{2}$.
These morphisms can be composed to give a morphism $c \circ \phi$ from $X$ to $A_{2}$.
The $A_{2}$-cohomology class $[c \circ \phi]$ of $c \circ \phi$ is called a \textbf{characteristic class (of $\phi$ w.r.t. $c$)}.
\end{enumerate}
Sometimes, it is convenient to also have terminology for cohomology when the coefficients are known to be an $n$-fold delooping of some object for some $n \in \mathbb{Z}$.
So, for $n \in \mathbb{Z}$, let
\begin{align*}
  A_{n}
  &:=
  \mathrm{B}^{n}A
\end{align*}
denote the $n$-fold delooping of $A$.
Then the $\infty$-groupoid of morphisms
\begin{align*}
  {}_{(\infty,1)}\mathbf{C}
  \left(
    X,
    A_{n}
  \right)
\end{align*}
that is, the $A_{n}$-cohomology of $X$, is called the \textbf{(degree-$n$) cohomology (of $X$ with coefficients in $A$)}.
One could go on defining cocycles and so on in this manner, but we will refrain from doing so here.
\\\\
After this mountain of terminology, we have to admit that this general idea of cohomology seems like quite a stretch compared to the motivation of singular homology we gave earlier.
Thus, one might believe that this idea of cohomology is a bit flimsily built.
But it isn't.
Quite the opposite - it encompasses almost everything that is commonly understood as cohomology.
Most importantly, it allows us to fully describe:
\begin{enumerate}
\item[(1)]
reduced axiomatic cohomology, which is not too hard to understand intuitively from the Brown representability theorem and what we have done for the singular case here.
\item[(2)]
non-abelian cohomology, which contains, e.g., sheaf cohomology.
\item[(3)]
twisted cohomology, which contains, e.g., differential cohomology.
\end{enumerate}
One just has to choose a fitting $(\infty,1)$-category.
Of course, this is just a claim here.
But take a look at the \cite{wiki-nlab0000} article: cohomology.
Besides a more detailed discussion of what we have provided here, it lists many references that should convince the wary reader that this is a highly sensible conception of cohomology.
