This is the main - and by far the longest - chapter of these notes.
It is devoted entirely to category theory.
However, we will develop it within a set theory rather than as a first-order theory.
Namely, in Tarski-Grothendieck (TG) set theory.
TG is (almost) ordinary mathematics as you likely know it.
The only difference is that we use {\glqq}Grothendieck universes{\grqq}.
This is because in category theory one often deals with large collections of things, and Grothendieck universes are a neat way to handle these (way better than the classes in von Neumann-Bernays-G\"{o}del (abbr. NBG) set theory or even informal classes).\footnote{See appendix \ref{chap:tg} for a formulation of TG.}
\\
On the one hand, we pay special attention to homotopy theory and higher category theory, albeit on a much more informal level than we do for ordinary category theory.
Homotopy theory and higher category theory will play a role in almost every section of this chapter.
But let us stress that it should be possible to understand a good part of this chapter without any prior knowledge of these theories (i.p. homotopy theory), as mentioned earlier.
\\
On the other hand, we pay special attention to physics.
Explicitly, we present a series of examples on so-called generalized spaces that directly relate to physics.
Implicitly, we have also chosen topics that we think are most important to physics while still being basic enough for an introduction.
\\\\
Let us now talk a bit about the sections of this chapter.
Of course, we present the most basic ideas of category theory as you would find them in any text on general category theory, but with certain emphases that are not so standard.
Let us present this as a list:
\begin{enumerate}
\item[$\bullet$]
The trinity in section \ref{sec:trinity}: categories, functors, natural transformations.
What sets these notes apart is the early focus on higher categories, which we already introduce in the trinity section \ref{sec:trinity}.
We will later see that this trinity is not as {\glqq}holy{\grqq} as one might expect at a first glance at category theory, but rather an expression of the fact that $0$, $1$, and $2$ are three natural numbers.
\item[$\bullet$]
Duality in section \ref{sec:duality}.
This is actually addressed in any serious text on category theory, since a lack of understanding can make things a little bloated.
Therefore, we have tried to emphasize this throughout these notes as much as possible.
\item[$\bullet$]
Constructions on a category in section \ref{sec:constoncat}.
We only discuss the ones important to us: product categories and comma categories.
There are quite a few other interesting ones we do not discuss, such as graphs.
For this section, there are certainly more complete sources.
\item[$\bullet$]
Universality in section \ref{sec:uni}.
This is the most important concept in category theory, which is why we discuss it extensively.
We strived to be as intuitive as possible (which we actually try to do throughout the entire text), with a special focus on parts that are particularly important to physics.
We start with what {\glqq}universality{\grqq} intuitively means, followed by the far-reaching Yoneda lemma waiting there for us.
It is no exaggeration to say that the Yoneda lemma dominates category theory in some sense.
You will hopefully comprehend what we mean after a perusal of section \ref{sec:uni}.
With limits and adjoints, we will explore arguably the most common {\glqq}universal constructions{\grqq}.
We will prove most of the standard theorems for these.
Then, a bit hidden in a subsubsection, we explore a further universal construction - Kan extensions - which is also of major importance.
They play a significant role, especially in homotopy theory.
\end{enumerate}
Well, this is what we consider the basics of category theory.
But that is not where we stop.
After the basics, it is time to look a bit at the big picture of category theory from a more modern perspective.
This is done in a section under a somewhat obscure title:
\begin{enumerate}
\item[$\bullet$]
Meta-ideas in section \ref{sec:metaidea}.
Category theory, and especially higher category theory, is surrounded by many more or less informal ideas (hence "meta-ideas").
We try to present these in a more or less informal style, depending on how sophisticated the idea is and how much effort is acceptable for our purposes.
In particular, you can find an informal introduction to higher category theory there, along with many references of interest.
\end{enumerate}
The last two sections are closely related to homotopy theory.
And since homotopy theory can be important in physics, we pay more attention to the subject than ordinary introductory texts on category theory usually do.
Let us briefly discuss the topics we mean.
\begin{enumerate}
\item[$\bullet$]
Simplicial sets in section \ref{sec:sset}.
In this section, we discuss how simplicial sets play a major role in homotopy theory.
In particular, we discuss how to use them in the classification of principal bundles by homotopy classes and cohomology ({\glqq}calculated{\grqq} with \v{C}ech cohomology).
\item[$\bullet$]
Fibrations in section \ref{sec:fibration}.
For an algebraic topologist or even a classical homotopy theorist, it is obvious that this has to do with homotopy theory.
We discuss a very general idea of fibrations and their duals (cofibrations), encompassing the notions from classical homotopy theory.
The highlight is a pretty formal definition of a {\glqq}stack{\grqq} which is essentially a homotopy-theoretic version of a sheaf.
\end{enumerate}
We hope we managed to give a reasonable overview of this chapter to save you from not seeing the forest for the trees.
