%\nocite{0b855cc5}
%\nocite{476fe2a3}
As humans, we claim that we experience nature as a smooth continuum.
Since it has proven very useful over the past few centuries to describe nature mathematically, it seems we need a mathematical idea of what a smooth continuum actually is.
Let's look at this idea a bit and see what it has to do with category theory.
\\
In Euclidean geometry, continuity is built-in.
It is a primitive concept.
One does not explain what the continuity of a line is, but rather, one is expected to know what it is from experience.
Now, Euclidean-style geometry is a bit limited as a theory to describe modern physics.
Therefore, around 1900, mathematicians gradually replaced Euclidean geometry with what is nowadays the widely accepted mathematical theory of everything: some version of set theory.
Set theory is all about collections of things, and one has to model everything one wants to describe in terms of these collections.
In particular, a smooth continuum has to be modeled like that.
One day, someone came up with the idea of using the well-known - but somehow mysterious - set of real numbers $\mathbb{R}$ as a model for a continuum.
Today, this is the broadly accepted model for a smooth continuum.
\\
But there is a potentially severe problem with that model in (ZF-like) set theories that use the axiom of choice: the Banach-Tarski paradox.
The paradox (on an intuitive level) is that one can decompose a unit ball in $\mathbb{R}^{3}$ into five disjoint sets and then reassemble these parts without any {\glqq}deformation{\grqq} into \underline{two} disjoint unit balls in $\mathbb{R}^{3}$.
This seems a bit odd under the interpretation of a smooth continuum.
Even worse, some physical theories that generally yield quite good results struggle with the continuum (in that sense). This is exactly the title and subject of the really worthwhile and easy-to-read notes \cite{476fe2a3}.
\\
One can now go ahead and try to mitigate these struggles in an orthodox way, or take a step back and explore different paths.
In the computer age, one conceivable way is to give up the continuum altogether and go with a discrete model of nature.
In fact, it is certainly within the realm of possibility that nature is not a continuum at all.
While a version of this finitistic point of view is pursued in \cite{0b855cc5}, we can head in another direction and take up the idea of built-in continuity.
This is where category theory comes into play: category theory provides an alternative to the traditional model $\mathbb{R}$ in the guise of topos theory\footnote{which is just category theory subjected to a few more axioms, as we will see}. This provides a synthetic theory that allows us to formally work with infinitesimals, just as physicists are used to doing (informally) anyway.
Furthermore, there is also so-called synthetic differential geometry, which seems to be a worthwhile replacement for ordinary differential geometry.
While we do not fully develop these ideas here, we provide the basis to understand them so that you can quickly pick them up from some other source.
Note that \cite{wiki-nlab0000} lists some literature on the subject.
\\
To wrap up this paragraph, let's just say that having a proper notion of a continuum is important when thinking about physics, because having one is an implicit assumption in physics, as we will see next.
