Historically, Eilenberg and Mac Lane observed that some functions in algebraic topology were more than mere functions.
These functions commuted with a certain kind of transformation - namely, the natural transformations, which we introduce in subsection \ref{sec:nt}.
This naturality property is often necessary in algebraic topology to make things work.
Anyway, to precisely formulate what they meant, they needed the notion of categories as an auxiliary concept.
But actually, they gave birth to a new theory: category theory.
While introducing categories from this perspective seems intuitive for algebraic topologists, and this is in fact how they are often introduced there, it is not really helpful for anyone else.
Even an algebraic topologist will eventually gain from the more modern approach we present.
\\
At some point in history, people observed that a category, defined as a certain set, is an interpretation of some first-order theory - called category theory - within set theory.
Hence, categories make sense without any surrounding set theory.
This is the more modern approach we just mentioned.
\\
Remember that in a set theory such as Zermelo-Fraenkel set theory with choice (abbr. ZFC) or Tarski-Grothendieck set theory (abbr. TG), the idea is that the only mathematical objects inhabiting the mathematical universe are sets.
Preformally, a set is seen as a collection of things.
Set theories like ZFC or TG then try to axiomatize what these collections are.
Directed paths - that is, paths which can only be traversed in one direction - are for category theory what sets are for ZFC and TG.
So, in category theory, we consider directed paths as the only mathematical objects inhabiting the mathematical universe.
\\
Now, what is special about the directed paths we have in mind?
How can we characterize them?
First of all, we symbolize a directed path by an arrow\footnote{indeed, some use the notion of arrows here rather than directed paths, as we do}
\begin{align*}
  \longrightarrow
\end{align*}
Certainly, a directed path has two different ends.
Namely:
\begin{enumerate}
\item[(1)]
a starting point - a source from which the arrow points away
\item[(2)]
a terminus (an ending point) - a target to which the arrow points.
\end{enumerate}
If a directed path starts where another one ends, we consider it sensible to be able to patch these directed paths together into a single directed path.
That is, we want to be able to compose directed paths.
In an arrow picture:
\[
\begin{tikzcd}[sep=large]
  \phantom{1}
  \arrow[shift left=1ex]{r}{}
  \arrow[shift right=1ex]{rr}{}
  &
  \phantom{1}
  \arrow[shift left=1ex]{r}{}
  &
  \phantom{1}
\end{tikzcd}
\]
For consistency, we should demand that if a given directed path is the composition of a first and a second directed path, then, of course, the terminus of the first directed path must be the starting point of the second.
Moreover, the starting point of the given directed path should be the starting point of the first directed path, while the terminus of the given directed path should be the terminus of the second one.
Next, this composition operation should not depend on the order in which we compose three (or more) directed paths.
This is expressed by the picture
\begin{align*}
  \left(
    \longrightarrow
    \quad
    \longrightarrow
  \right)
  \quad
  \longrightarrow
  \qquad
  &=
  \qquad
  \longrightarrow
  \quad
  \left(
    \longrightarrow
    \quad
    \longrightarrow
  \right)
\end{align*}
What is not clear so far is which mathematical objects the starting point and terminus of a directed path should be.
Since the only mathematical objects we believe to exist here are directed paths, they must clearly be directed paths themselves.
Hence, for any given directed path, we should demand the existence of two directed paths which, when composed with the given directed path at its starting point and terminus respectively, reproduce the original directed path.
That is, we have directed paths
\begin{align*}
  \rightharpoonup
\end{align*}
and
\begin{align*}
  \rightharpoondown
\end{align*}
such that
\begin{align*}
  \rightharpoonup
  \quad
  \longrightarrow
  \qquad
  &=
  \qquad
  \longrightarrow  
  \qquad
  =
  \qquad
  \longrightarrow
  \quad
  \rightharpoondown
\end{align*}
These seem to be reasonable choices since, by repeating the process of composing such directed paths, nothing happens.
These identity directed paths are somehow stationary.
The starting point and terminus of an identity directed path are clearly the same.
All this can be interpreted to mean that an identity directed path points to itself, and the starting point and terminus, respectively, do not change.
\\
To encode this formally in a first-order theory, we need:
\begin{enumerate}
\item[(1)]
a unary function symbol
\begin{align*}
  \mathrm{s}
\end{align*}
intended to represent a function mapping an arbitrary directed path to the directed path encoding the starting point (or, say, the source of the arrow)
\item[(2)]
a unary function symbol
\begin{align*}
  \mathrm{t}
\end{align*}
intended to represent a function mapping an arbitrary directed path to the directed path encoding the terminus (or, say, the target of the arrow)
\item[(3)]
a $3$-ary relation symbol
\begin{align*}
  \mathrm{c}
\end{align*}
intended to represent a relation of three arguments checking if the directed path in the third argument is the composition of the preceding two
\end{enumerate}
As variables for directed paths, we take $a,a_{1},a_{2},\ldots$ and so on.
Then the properties we assume our directed paths to have are (formally) expressed by the following list:
\begin{enumerate}
\item[(CT1)]
We demand a unique composition of $a_{1}$ and $a_{2}$ if the terminus of $a_{1}$ is the starting point of $a_{2}$.
As a formula
\begin{align*}
  \mathrm{t}(a_{1})
  =
  \mathrm{s}(a_{2})
  \qquad
  &\Rightarrow
  \qquad
  \exists!
a
  \left(
    \mathrm{c}(a_{1},a_{2},a)
  \right)
\end{align*}
\item[(CT2)]
A necessary condition for $a$ to be the composition of $a_{1}$ and $a_{2}$ is that the terminus of $a_{1}$ is the starting point of $a_{2}$, and that the starting point of $a$ is the starting point of $a_{1}$, while the terminus of $a$ should be the terminus of $a_{2}$.
As a formula
\begin{align*}
  \mathrm{c}(a_{1},a_{2},a)
  \qquad
  &\Rightarrow
  \qquad
  \left(
    \mathrm{t}(a_{1})
    =
    \mathrm{s}(a_{2})
    \quad
    \land
    \quad
    \mathrm{s}(a)
    =
    \mathrm{s}(a_{1})
    \quad
    \land
    \quad
    \mathrm{t}(a)
    =
    \mathrm{t}(a_{2})
  \right)
\end{align*}
\item[(CT3)]
There should be an associative law; that is, given directed paths $a_{1},a_{2},a_{3}$ such that $\mathrm{t}(a_{1}) = \mathrm{s}(a_{2})$ as well as $\mathrm{t}(a_{2}) = \mathrm{s}(a_{3})$, then it should not matter whether we first compose $a_{1}$ with $a_{2}$ and then the result with $a_{3}$, or if we compose $a_{1}$ with the result of composing $a_{2}$ with $a_{3}$.
As a formula 
\begin{align*}
  \left(
    \mathrm{c}(a_{1},a_{2},a_{4})
    \quad
    \land
    \quad
    \mathrm{c}(a_{2},a_{3},a_{5})
  \right)
  \qquad
  &\Rightarrow
  \qquad
  \left(
    \mathrm{c}(a_{4},a_{3},a)
    \quad
    \Leftrightarrow
    \quad
    \mathrm{c}(a_{1},a_{5},a)
  \right)
\end{align*}
\item[(CT4)]
The starting point of a directed path $a$ should be a directed path whose starting point and terminus are equal, and a corresponding statement should hold for the terminus of $a$.
As a formula
\begin{align*}
  \mathrm{s}(\mathrm{s}(a))
  =
  \mathrm{s}(a)
  =
  \mathrm{t}(\mathrm{s}(a))
  \qquad
  &\land
  \qquad
  \mathrm{s}(t(a))
  =
  \mathrm{t}(a)
  =
  \mathrm{t}(\mathrm{t}(a))
\end{align*}

\item[(CT5)]
There should be an identity law; that is, composing the starting point of a directed path $a$ with $a$ should give $a$, while composing $a$ with its terminus should give $a$, too.
As a formula
\begin{align*}
  \mathrm{c}(\mathrm{s}(a),a,a)
  \qquad
  &\land
  \qquad
  \mathrm{c}(a,\mathrm{t}(a),a)
\end{align*}
\end{enumerate}
The first-order theory stated in this way is called category theory and can be regarded as a theory of directed paths (in the sense of the paths in homotopy theory, but with a direction).
But, as usual in mathematics, category theory is not done in this formal first-order manner.
One rather builds a model of the theory of discourse within a theory that is well-understood, well-accepted, and universal enough.
This is usually a set theory as described by ZFC or TG.
The model is built as an interpretation in set theory.
One then reasons within this theory, but usually in a much more informal manner.
And we do the same in subsection \ref{sec:cat}, within a mathematical universe of sets that obeys the rules of TG.
\\
It is pretty apparent that functions $f = (Y_{1},Y_{2},\Gamma_{f})$ as $3$-tuples consisting of the domain $Y_{1}$, the codomain $Y_{2}$, and the graph $\Gamma_{f}$ have, among other properties, the same ones as our directed paths.
The identity function of a set contains essentially just the information about which set it is the identity function for.
This suggests that the starting point of a function regarded only w.r.t.
its directed path aspect is just its domain, while the terminus is just its codomain.
If $\circ$ denotes the usual function composition and $\mathrm{dom}_{\mathrm{f}}$ denotes taking the domain of a function, while $\mathrm{cod}_{\mathrm{f}}$ denotes taking the codomain of a function, then setting
\begin{align*}
  \mathrm{s}
  &:=
  \mathrm{dom}_{\mathrm{f}}
  \\
  \mathrm{t}
  &:=
  \mathrm{cod}_{\mathrm{f}}
  \\
  \mathrm{c}(f_{1},f_{2},f)
  \quad
  &:\Leftrightarrow
  \quad
  f
  =
  f_{2}
  \circ
  f_{1}
\end{align*}
makes the formulas (CT1)-(CT5) true.
$f,f_{1},f_{2}$ are clearly function variables here.
Thus, one could have abstracted category theory from function composition.
But note that category theory is not a formalization of the function idea, since the crucial part of the function idea is \underline{how} elements of a collection are mapped to elements of another collection.
Yet it is common to adjust terminology to the function case.
This has historical reasons.
Originally, categories were thought of as sets of structure-preserving functions.
We will also adapt to this historical inaccuracy (or philosophical stance where set theory is the theory of everything and category theory is only reasonable if interpreted within it) and adjust our terminology:
\begin{enumerate}
\item[(1)]
directed path is synonymous with arrow, which in turn is synonymous with morphism\footnote{this terminology is dealt with in subsection \ref{sec:cat} and might not be clear yet, but it has to do with the original examples of categories}
\item[(2)]
starting point is synonymous with source, which in turn is synonymous with domain
\item[(3)]
terminus is synonymous with target, which in turn is synonymous with codomain
\item[(4)]
composition stays composition
\end{enumerate}
Now there is another thing one can do.
Since category theory is a first-order theory, we can add more axioms.
For example, some that bring arrows closer to the idea of functions.
This idea is very fruitful and culminates in topos theory, which adds some axioms such that the resulting universe of arrows makes the identity arrows behave like sets.
This is how topos theory provides a number of foundations for mathematics.
In particular, one can add axioms to topos theory such that the resulting theory is sufficiently close to ZFC for the purposes of ordinary\footnote{it lacks a version of the replacement axiom, but this is not really a constraint, and if still needed, there is an arrow version of it that can be added} mathematics.
It is called ETCS, abbreviating {\glqq}Elementary Theory of the Category of Sets{\grqq}.
Actually, theories like ETCS are even better suited from a practical perspective, since they capture only the structural aspects of sets and not the material ones.
This means that the elements of a set are just elements and not necessarily sets themselves, as they are in material set theories such as ZFC or TG.
Moreover, we can only compare elements of a given set for equality, and not elements of different sets in general.
We will return to ETCS later in section \ref{sec:metaidea}, once we know enough about categories.
On the whole, this shows that category theory is a very fundamental idea with a deep impact on mathematics and, more astonishingly, on physics too, as we will allude to here and there throughout the notes.
\\
Last but not least, note that a directed path can be regarded as a way of going from one identity directed path to another.
Hence, directed paths kind of structure the collection of identity directed paths.
This is in contrast to the fact that a set is a collection without any relationship among its members.
It is, roughly speaking, just a bag of points.
A set can be regarded as a category with only identity directed paths, and so a category is something more general than a set, with sets being just a lower-dimensional\footnote{this terminology will become clear later} discrete special case.
This is further evidence that one should consider category theory separately from set theory.
The next question, then, is whether we can think up a theory that structures the collection of all directed paths in a similar vein.
That is to say: is there some kind of 2-directed path with a starting point and terminus that are identity 2-directed paths, which in turn stand for ordinary ($1$-)directed paths?
And if so, can we go higher to $3$-directed paths, or even $n$-directed paths for some natural number $n$?
This leads to the idea of higher category theory and the idea of replacing sets as fundamental mathematical objects with higher categories.
This would yield a {\glqq}directed homotopy theory{\glqq} in our interpretation, as will hopefully become clear in these notes.
However, this has not been very successful yet.
But the case where all directed paths are reversible seems more promising.
A directed path is reversible if there is a directed path which, when composed with the original one in any way, results in an identity directed path.
Categories where all directed paths are reversible are called groupoids, and we will briefly discuss them in subsection \ref{sec:nt}.
This should then yield just ordinary homotopy theory with ordinary (undirected) paths.
The more successful foundation attempt we are talking about is the Univalent Foundations Program with its Homotopy Type Theory, as described in the HoTT book \cite{1ba1603e} as {\glqq}synthetic{\grqq} homotopy theory.
We abbreviate this as UFP-HoTT when referring to it.
The basic mathematical objects are higher groupoids - so-called $\infty$-groupoids - or, equivalently, homotopy types.
We will discuss this higher directed path idea more thoroughly in subsection \ref{sec:nt} and again in section \ref{sec:metaidea}.
\\\\
But first, we have to understand categories better.
A category alone is not worth much without the notions of functor and natural transformation.
These, together with categories, make up the trinity of category theory.
After shining some light on categories modeled as sets in subsection \ref{sec:cat}, we deal with structure-preserving functions between categories called functors in subsection \ref{sec:func}, before we deal with structure-preserving functions between functors called natural transformations in subsection \ref{sec:nt}.
