%\nocite{c55c71e8}
%\nocite{e837ef86}
%\nocite{a565d200}
%\nocite{dc6f686f}
%\nocite{1ba1603e}
%\nocite{52fbba46}
%\nocite{8b5861fc}
%\nocite{wiki-nlab0000}
%\nocite{wiki-pedia0en}
These notes are intended as an introductory text on category theory in the context of physics.
The idea of these notes is to serve as an introductory text on category theory and how to apply it to modern physics.
For that purpose, we develop category theory alongside physics in the main part of these notes (chapter \ref{chap:initcontext}), surrounded by chapters providing physical context.
Chapter \ref{chap:initcontext}, preceding the category part, tries to motivate the use of category theory in physics, while chapter \ref{chap:termcontext}, following the category part, discusses what to do with the gained knowledge, eventually leading to an account of physics \cite{a565d200} leveraging higher category theory.
\\
For reasons of modularity, we refrain from writing a more thorough introduction, deferring it to the other chapters.
Instead, we'll just talk about the mathematical requirements to understand the notes and a few style things in the rest of this chapter.
\\\\
Actually, the bar is quite low for reading these notes.
While the ideal reader has a solid mathematical background (let's just say undergraduate level, at least), we claim that a good chunk of these notes is understandable with way less mathematical knowledge.
This is because category theory can be regarded as being at the very foundation of mathematics.
So the target audience is anyone with some basic mathematical knowledge (we will clarify {\glqq}what{\grqq} in a moment), possibly with an interest in physics.
\\
Now, what do we require you to know? Well, there are several levels on which you can read these notes:
\begin{enumerate}
\item[(1)]
If you want to understand the category theory part only, then there is not much you are required to know already.
It suffices to be familiar with very basic mathematics, which we believe someone studying mathematics at a university for a year or so would be:
\begin{enumerate}
\item[$\bullet$]
Reasoning in classical logic about mathematical objects.
This, in particular, includes an understanding of first-order theories on an intuitive level.
That is, you should be able to read and understand formulas such as $\exists x \forall y(y \in x \Rightarrow \ldots)$, and you should have a feel for what a mathematical proof is.
\item[$\bullet$]
Set theory and some fundamental constructions in set theory.
You are not required to know formal set theory (such as ZFC), but only what one can do with sets in ordinary mathematics on an intuitive level.
In particular, you should know about unions, intersections, ordered pairs, and perhaps some other fundamental stuff we forgot to list here.
\item[$\bullet$]
Relations and particularly equivalence relations.
\item[$\bullet$]
Functions.
Here we mean functions between sets.
At this point, you should note that we sometimes differentiate functions from {\glqq}assignments{\grqq}\footnote{This is a non-standard term (sometimes people speak of definable functions in this context)} terminologically.
In our terminology, assignments not only map the elements of a set - an object of the mathematical universe - to elements of some other set, but also map (a part of) the objects in the mathematical universe to objects of the mathematical universe.
\item[$\bullet$]
Ordered sets.
We require knowledge about preordered sets, partially ordered sets, totally ordered sets, and well-ordered sets.
\end{enumerate}
This is actually enough for most of the notes.
Yet, it is certainly better to know more about mathematics for a deeper understanding.
For example, an understanding of what mathematics actually is (there are different ideas on that) is certainly helpful, though it is not easy to grasp, and especially when you're just starting out, it might raise more questions than it answers.
However, you can approach the material from another level to improve your understanding of these notes.
Many of our examples originate in certain traditional fields of mathematics: algebra and topology.
A proper understanding of these fields will help you understand the examples, and thus category theory, better.
We will discuss most of the things we need from algebra and topology for the sake of self-containment.
But don't expect an overly pedagogical discussion.
So it would be good to already know a bit about algebra, topology, and perhaps the foundations of mathematics.
\item[(2)]
If you want to understand the entire category theory part, then there is no getting around learning homotopy theory.
Homotopy theory is deeply linked to category theory and higher category theory.
This is one of the major aspects of these notes, as you will very soon realize.
Also, cohomology will play a big role in these notes.
We don't want to spoil too much here, so we'll just say that a perfectly prepared reader is already familiar with some traditional algebraic topology.
\item[(3)]
If you also want to understand the physical context, then you should know a bit about basic physics and quite a bit about differential geometry.
\end{enumerate}
Note that we sometimes write terms in \textit{italics} when the reader isn't expected to already know them.
Moreover, we want to explicitly emphasize that you should just skip things you don't understand.
You should still be able to follow what is going on.
At least, that's our intention.
\\
Last but not least, note that we provide references throughout the notes for some of the stuff we discussed as requirements.
But there are a few core sources that the content of these notes is based on, which we want to highlight explicitly.
The obvious one is wikipedia \cite{wiki-pedia0en}.
Probably everybody uses it as a general-purpose source, and so do we.
But for (higher) category theory and many related topics, there is another great resource: the nLab \cite{wiki-nlab0000}.
If you are seriously interested in what we're doing here, then this is your best friend.
The category theory we cover is based on the nLab and on the following three sources:
\begin{enumerate}
\item[$\bullet$]
Mac Lane's traditional book \cite{e837ef86}
\item[$\bullet$]
Leinster's introductory book \cite{dc6f686f}
\item[$\bullet$]
Riehl's modern book \cite{52fbba46}
\end{enumerate}
The {\glqq}wisdom{\grqq} in these notes arguably comes from Mac Lane and Moerdijk's book on sheaves and topoi \cite{c55c71e8}.
Lastly, we shouldn't forget about homotopy theory:
\begin{enumerate}
\item[$\bullet$]
Hatcher's well-known algebraic topology book \cite{8b5861fc} for a traditional view
\item[$\bullet$]
The Univalent Foundations Program book on homotopy type theory \cite{1ba1603e} for a modern synthetic approach
\end{enumerate}
Most of these sources are heavily cited in these notes.
\\\\
Now we need to talk a bit about the style of this text.
Our focus is on intuition, but also on being as precise as possible.
We tried to motivate everything on an intuitive level on the one hand, while additionally being as formal as needed on the other.
This is because being fully formal is unambiguous, but often hard for humans to understand.
So we think it's better to babble a bit about things in natural language, while remaining formal enough just in case the babbling leaves room for misconception.
We hope what we have written is explicit and comprehensible so that you can read through it quickly without puzzling over the phrasing too much.
The price we pay for this strategy is taking up a large amount of space for comparatively little content.
Also note that we are usually way more formal in chapter \ref{chap:cattg} than in all the other chapters.
\\
Mathematical definitions are \textbf{bold} and usually presented in the style {\glqq}$\mathcal{F}$ is called \textbf{NAME OF THE FORMULA $\mathcal{F}$}{\grqq} or {\glqq}$\mathcal{F}_{1}$ is \textbf{NAME OF THE FORMULA $\mathcal{F}_{1}$} if $\mathcal{F}_{2}${\grqq}, where the tokens $\mathcal{F},\mathcal{F}_{1},\mathcal{F}_{2}$ are variables for formulas.
In the second case, $\mathcal{F}_{2}$ is often only semi-formal in practice.
We also use parentheses in the \textbf{bold} text to indicate which parts of the name we allow to be implicit.
So, when referring to a definition, it suffices to say the part not in parentheses (and perhaps parts of the parenthesized name) as long as we don't have to fear misunderstandings.
Mathematical statements are made and proved in the running text.
But if we want to refer to it later, or if the statement is of particular importance, we use numbered theorem environments followed by (unnumbered) proof environments that terminate with a $\square$.
We think this provides an ideal mix of comprehension and readability.
The most important proofs in ordinary category theory are done in a quite explicit fashion.
In other places, we try to provide references containing sufficient proof for the statements in question.
But we frequently leave proofs as an exercise for the reader if they are not that important, or if they are easy, tedious, and unenlightening.
And sometimes we just sketch a proof (without any particularly convincing reason).
A final word on examples: they are treated in the same fashion as (long) statements (since they usually are).
However, we want to emphasize that they are rarely just for illustration purposes in these notes, so don't just skip them carelessly if you think you've already understood the aspect they illustrate.
